---
title: "MiSTer Controller Latency"
author: "Porkchop Express, Lemonici"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

<style>
@import url("https://fonts.googleapis.com/css2?family=Space+Grotesk:wght@400;500;600;700&family=IBM+Plex+Mono:wght@400;500&display=swap");

:root {
  --bg: #32008d;
  --bg-accent-a: rgba(230, 255, 30, 0.28);
  --bg-accent-b: rgba(255, 255, 255, 0.12);
  --text: #f3edff;
  --muted: #d8c9ff;
  --card: rgba(34, 14, 92, 0.72);
  --card-solid: rgba(29, 12, 80, 0.92);
  --panel: rgba(41, 16, 110, 0.72);
  --border: rgba(230, 255, 30, 0.2);
  --border-strong: rgba(230, 255, 30, 0.42);
  --tab-idle: #ecdeff;
  --shadow: 0 18px 45px rgba(17, 3, 48, 0.45);
  --shadow-soft: 0 6px 20px rgba(11, 2, 34, 0.38);
  --ring: rgba(230, 255, 30, 0.38);
  --primary: #5000DC;
  --primary-strong: #6f2cff;
  --accent: #E6FF1E;
  --accent-strong: #f3ff74;
  --cta: linear-gradient(135deg, #E6FF1E 0%, #bfd900 100%);
  --chip-bg: rgba(38, 14, 101, 0.86);
  --chip-border: rgba(230, 255, 30, 0.22);
  --table-row: rgba(39, 16, 103, 0.8);
  --plot-bg: #2b0a78;
  --header-grad: linear-gradient(120deg, rgba(230, 255, 30, 0.22), rgba(255, 255, 255, 0.08));
  --mono: "IBM Plex Mono", ui-monospace, SFMono-Regular, Menlo, monospace;
}

html[data-theme="dark"] {
  --bg: #3f1e8f;
  --bg-accent-a: rgba(230, 255, 30, 0.24);
  --bg-accent-b: rgba(255, 255, 255, 0.1);
  --text: #f4efff;
  --muted: #d5c9ff;
  --card: rgba(21, 8, 56, 0.9);
  --card-solid: #1a0b45;
  --panel: rgba(23, 9, 62, 0.9);
  --border: rgba(230, 255, 30, 0.24);
  --border-strong: rgba(230, 255, 30, 0.44);
  --tab-idle: #e7dcff;
  --shadow: 0 22px 55px rgba(8, 2, 24, 0.58);
  --shadow-soft: 0 10px 28px rgba(7, 2, 18, 0.46);
  --ring: rgba(230, 255, 30, 0.45);
  --primary: #a783ff;
  --primary-strong: #c2a9ff;
  --accent: #E6FF1E;
  --accent-strong: #f7ff9a;
  --cta: linear-gradient(135deg, #E6FF1E 0%, #c2db00 100%);
  --chip-bg: rgba(28, 11, 73, 0.94);
  --chip-border: rgba(230, 255, 30, 0.25);
  --table-row: rgba(25, 10, 66, 0.9);
  --plot-bg: #1f0c52;
  --header-grad: linear-gradient(120deg, rgba(230, 255, 30, 0.24), rgba(123, 75, 255, 0.16));
}

* {
  box-sizing: border-box;
}

body {
  font-family: "Space Grotesk", "Segoe UI", "Trebuchet MS", "Helvetica Neue", sans-serif;
  background: var(--bg);
  color: var(--text);
  transition: background 0.25s ease, color 0.25s ease;
}

body::before {
  content: "";
  position: fixed;
  inset: 0;
  pointer-events: none;
  background:
    radial-gradient(1200px 540px at 10% -5%, var(--bg-accent-a), transparent 60%),
    radial-gradient(1000px 500px at 98% 0%, var(--bg-accent-b), transparent 62%);
  z-index: -1;
}

a {
  color: var(--accent);
}

a:hover {
  color: var(--accent-strong);
}

.main-container {
  max-width: 1580px !important;
  margin-left: auto;
  margin-right: auto;
  padding: 20px 20px 28px;
}

#TOC {
  margin: 0 !important;
  padding: 10px !important;
  border: 1px solid var(--border) !important;
  border-radius: 16px !important;
  background: var(--panel) !important;
  box-shadow: var(--shadow-soft) !important;
}

div.tocify {
  position: sticky !important;
  top: 10px !important;
  width: 100% !important;
  max-width: 320px !important;
  max-height: calc(100vh - 24px) !important;
  overflow-y: auto !important;
  background: transparent !important;
  margin-left: 0 !important;
}

.tocify .tocify-header,
.tocify .tocify-item {
  line-height: 1.35 !important;
}

.tocify .list-group-item {
  border: 1px solid transparent !important;
  border-radius: 10px !important;
  margin-bottom: 5px;
  padding: 8px 10px !important;
  background: transparent !important;
  color: var(--muted) !important;
  font-weight: 600;
}

.tocify .list-group-item:hover {
  background: rgba(230, 255, 30, 0.12) !important;
  color: var(--text) !important;
  border-color: rgba(230, 255, 30, 0.34) !important;
}

.tocify .list-group-item.active,
.tocify .list-group-item.active:hover,
.tocify .list-group-item.active:focus {
  color: var(--text) !important;
  background: linear-gradient(90deg, rgba(230, 255, 30, 0.2), rgba(123, 75, 255, 0.22)) !important;
  border-color: rgba(230, 255, 30, 0.38) !important;
  box-shadow: inset 3px 0 0 var(--accent);
}

.tocify-subheader .list-group-item {
  font-size: 0.92rem !important;
  padding-left: 16px !important;
}

#header {
  position: relative;
  border: 1px solid var(--border);
  border-radius: 22px;
  background: var(--header-grad);
  box-shadow: var(--shadow-soft);
  padding: 28px 24px 22px;
  margin-bottom: 24px;
  backdrop-filter: blur(6px);
}

#header h1.title {
  margin-top: 0;
  margin-bottom: 6px;
  font-weight: 700;
  letter-spacing: 0.01em;
  font-size: clamp(1.65rem, 2.2vw, 2.45rem);
}

#header .author {
  color: var(--muted);
  margin-bottom: 0;
}

.tab-content > .tab-pane {
  line-height: 1.6;
}

.nav-tabs {
  border-bottom: 1px solid var(--border);
  margin-bottom: 18px;
}

.nav-tabs > li > a {
  font-size: 1.02rem;
  font-weight: 600;
  padding: 12px 18px;
  border-radius: 12px 12px 0 0;
  color: var(--tab-idle);
  transition: background 0.18s ease, color 0.18s ease, border-color 0.18s ease;
  border: 1px solid transparent;
}

.nav-tabs > li > a:hover {
  background: var(--panel);
  border-color: var(--border);
}

.nav-tabs > li.active > a,
.nav-tabs > li.active > a:hover,
.nav-tabs > li.active > a:focus {
  color: var(--text);
  background: var(--card);
  border-color: var(--border);
  border-bottom-color: transparent;
}

.bg-source-note {
  margin: 4px 0 18px;
  border: 1px solid var(--border);
  background: var(--panel);
  color: var(--muted);
  border-radius: 14px;
  padding: 12px 14px;
  font-size: 0.92rem;
  box-shadow: var(--shadow-soft);
}

.bg-hero {
  position: relative;
  border: 1px solid var(--border);
  border-radius: 16px;
  padding: 16px 16px 14px;
  margin: 6px 0 18px;
  background:
    linear-gradient(135deg, rgba(230, 255, 30, 0.16), rgba(80, 0, 220, 0.16)),
    var(--panel);
  box-shadow: var(--shadow-soft);
}

.bg-hero-title {
  font-size: clamp(1.12rem, 2vw, 1.42rem);
  font-weight: 700;
  color: var(--text);
  margin-bottom: 3px;
}

.bg-hero-sub {
  margin: 0;
  color: var(--muted);
  font-size: 0.94rem;
}

.bg-hero-actions {
  display: flex;
  flex-wrap: wrap;
  gap: 8px;
  margin-top: 12px;
}

.bg-hero-btn {
  display: inline-flex;
  align-items: center;
  border: 1px solid rgba(230, 255, 30, 0.4);
  border-radius: 999px;
  padding: 6px 12px;
  font-size: 0.82rem;
  font-weight: 700;
  text-decoration: none;
  color: #2a2d07;
  background: var(--accent);
}

.bg-hero-btn:hover {
  text-decoration: none;
  border-color: rgba(230, 255, 30, 0.62);
  background: var(--accent-strong);
}

.bg-hero-meta {
  margin-top: 12px;
  display: flex;
  flex-wrap: wrap;
  gap: 8px;
}

.bg-hero-meta span {
  display: inline-flex;
  border: 1px solid var(--border);
  border-radius: 999px;
  padding: 4px 10px;
  font-size: 0.75rem;
  color: var(--muted);
  background: var(--card-solid);
  font-family: var(--mono);
}

.bg-kpi-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(180px, 1fr));
  gap: 12px;
  margin: 8px 0 18px;
}

.bg-kpi {
  border: 1px solid var(--border);
  border-radius: 14px;
  padding: 12px 14px;
  background: var(--panel);
  box-shadow: var(--shadow-soft);
}

.bg-kpi .label {
  font-size: 0.74rem;
  color: var(--muted);
  text-transform: uppercase;
  letter-spacing: 0.09em;
  margin-bottom: 4px;
}

.bg-kpi .value {
  font-size: 1.2rem;
  font-weight: 700;
  color: var(--accent);
}

.bg-filter-panel {
  background: var(--panel);
  border: 1px solid var(--border);
  border-radius: 18px;
  padding: 24px 24px 20px;
  margin-top: 8px;
  margin-bottom: 24px;
  box-shadow: var(--shadow);
  backdrop-filter: blur(7px);
}

.bg-filter-panel h4 {
  margin: 0 0 10px;
  font-size: 0.78rem;
  font-weight: 700;
  text-transform: uppercase;
  letter-spacing: 0.09em;
  color: var(--muted);
}

.bg-filter-group {
  margin-bottom: 18px;
}

.bg-filter-group:last-child {
  margin-bottom: 0;
}

.bg-filter-controls {
  display: grid;
  grid-template-columns: minmax(230px, 1fr) auto auto auto auto auto;
  gap: 10px;
  margin-bottom: 16px;
  align-items: center;
}

.bg-filter-search {
  min-width: 0;
}

.bg-filter-search input,
.bg-filter-sort select,
.bg-density-btn,
.bg-theme-btn,
.bg-reset-btn {
  min-height: 42px;
  border: 1px solid var(--border);
  border-radius: 10px;
  background: var(--card-solid);
  color: var(--text);
  transition: border-color 0.15s ease, box-shadow 0.15s ease, background 0.15s ease;
}

.bg-filter-search input {
  width: 100%;
  padding: 10px 12px;
  font-size: 0.94rem;
}

.bg-filter-search input:focus,
.bg-filter-sort select:focus,
.bg-density-btn:focus,
.bg-theme-btn:focus,
.bg-reset-btn:focus {
  outline: none;
  border-color: var(--accent);
  box-shadow: 0 0 0 3px var(--ring);
}

.bg-filter-sort select {
  padding: 8px 10px;
  font-size: 0.92rem;
}

.bg-density-btn,
.bg-theme-btn,
.bg-reset-btn {
  padding: 9px 12px;
  font-size: 0.9rem;
  font-weight: 600;
  white-space: nowrap;
}

.bg-density-btn:hover,
.bg-theme-btn:hover,
.bg-reset-btn:hover {
  border-color: var(--border-strong);
}

.filter-btn {
  display: inline-block;
  padding: 8px 14px;
  margin: 4px 6px 4px 0;
  border: 1px solid var(--border);
  border-radius: 999px;
  background: var(--card-solid);
  color: var(--text);
  font-size: 0.85rem;
  font-weight: 600;
  cursor: pointer;
  transition: all 0.15s ease;
  line-height: 1.2;
}

.filter-btn:hover {
  border-color: var(--border-strong);
  color: var(--text);
  background: var(--panel);
}

.filter-btn.active {
  background: var(--accent);
  color: #2a2d07;
  border-color: rgba(230, 255, 30, 0.72);
  box-shadow: 0 8px 18px rgba(230, 255, 30, 0.25);
}

.filter-btn.active[data-dim="category"] { background: var(--accent); }
.filter-btn.active[data-dim="connection"] {
  background: var(--accent-strong);
  color: #2a2d07;
  box-shadow: 0 8px 18px rgba(230, 255, 30, 0.3);
}
.filter-btn.active[data-dim="platform"] {
  background: linear-gradient(135deg, var(--accent), var(--primary-strong));
  color: #f7f7ff;
}
.filter-btn.active[data-dim="face"],
.filter-btn.active[data-dim="home"] {
  background: linear-gradient(135deg, var(--accent), var(--accent-strong));
  color: #2a2d07;
}
.filter-btn.active[data-dim="analog"] {
  background: linear-gradient(135deg, var(--accent), #bdf100);
  color: #2a2d07;
}

.bg-counter {
  font-size: 0.9rem;
  color: var(--muted);
  margin-top: 4px;
  margin-bottom: 14px;
  font-family: var(--mono);
}

.bg-recent-strip {
  display: flex;
  overflow-x: auto;
  gap: 10px;
  padding: 6px 4px 12px;
  margin-bottom: 22px;
  -webkit-overflow-scrolling: touch;
}

.bg-recent-strip::-webkit-scrollbar {
  height: 6px;
}

.bg-recent-strip::-webkit-scrollbar-thumb {
  background: var(--border-strong);
  border-radius: 6px;
}

.bg-recent-chip {
  flex: 0 0 auto;
  display: flex;
  align-items: center;
  gap: 8px;
  background: var(--chip-bg);
  border: 1px solid var(--chip-border);
  border-radius: 999px;
  padding: 7px 14px;
  font-size: 0.84rem;
  white-space: nowrap;
  color: var(--text);
}

.bg-recent-chip .chip-badge {
  font-weight: 700;
  padding: 2px 9px;
  border-radius: 999px;
  font-size: 0.78rem;
}

.bg-card-grid {
  display: flex;
  flex-direction: column;
  gap: 12px;
  margin-bottom: 28px;
}

.bg-card {
  position: relative;
  overflow: hidden;
  background: var(--card);
  border: 1px solid var(--border);
  border-radius: 16px;
  padding: 16px 18px 14px;
  box-shadow: var(--shadow-soft);
  transition: transform 0.18s ease, box-shadow 0.18s ease, border-color 0.18s ease;
  display: grid;
  grid-template-columns: auto minmax(0, 1fr) auto;
  grid-template-areas:
    "rank title metrics"
    "rank mode mode"
    "rank meter meter"
    "rank buy buy"
    "rank details details";
  column-gap: 14px;
  row-gap: 10px;
  align-items: center;
  opacity: 0;
  transform: translateY(8px);
  animation: cardReveal 0.45s cubic-bezier(0.2, 0.7, 0.2, 1) forwards;
  animation-delay: calc(var(--stagger, 0) * 28ms);
}

.bg-card::after {
  content: "";
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  height: 3px;
  background: linear-gradient(90deg, var(--accent), var(--primary-strong));
  opacity: 0.6;
}

.bg-card:hover {
  transform: translateY(-3px);
  border-color: var(--border-strong);
  box-shadow: var(--shadow);
}

@keyframes cardReveal {
  from {
    opacity: 0;
    transform: translateY(8px);
  }
  to {
    opacity: 1;
    transform: translateY(0);
  }
}

.bg-card-rank {
  grid-area: rank;
  align-self: start;
  padding-top: 2px;
  font-family: var(--mono);
  font-size: 1.22rem;
  font-weight: 600;
  color: var(--muted);
}

.bg-card-title {
  grid-area: title;
  display: flex;
  align-items: center;
  justify-content: space-between;
  gap: 10px;
  min-width: 0;
}

.bg-card-name {
  font-size: 1.36rem;
  font-weight: 700;
  color: var(--text);
  line-height: 1.35;
  min-width: 0;
}

.bg-card-connection-badge {
  flex: 0 0 auto;
  white-space: nowrap;
  color: var(--accent) !important;
}

.bg-card-metrics {
  grid-area: metrics;
  text-align: right;
  white-space: nowrap;
  font-size: 1.34rem;
  font-weight: 700;
  margin: 0;
  color: var(--accent);
}

.bg-card-mode {
  grid-area: mode;
  font-size: 0.9rem;
  color: var(--muted);
  margin-top: -3px;
}

.bg-metric-sep {
  color: var(--muted);
  margin: 0 0.28em;
}

.bg-card-probability {
  grid-area: meter;
  margin-top: 2px;
}

.bg-prob-track {
  position: relative;
  overflow: hidden;
  height: 12px;
  border-radius: 999px;
  border: 1px solid var(--border);
  background: rgba(230, 255, 30, 0.16);
}

.bg-prob-fill {
  height: 100%;
  border-radius: 999px;
  box-shadow: 0 0 0 1px rgba(0, 0, 0, 0.08), 0 0 10px rgba(0, 0, 0, 0.08);
}

.bg-tag {
  display: inline-block;
  padding: 5px 12px;
  border-radius: 999px;
  font-size: 0.88rem;
  font-weight: 700;
  line-height: 1.35;
  border: 1px solid transparent;
}

.bg-tag-tier-a { background: rgba(35, 167, 102, 0.16); color: #0a7d49; border-color: rgba(35, 167, 102, 0.35); }
.bg-tag-tier-b { background: rgba(235, 167, 42, 0.16); color: #9b6200; border-color: rgba(235, 167, 42, 0.35); }
.bg-tag-tier-c { background: rgba(231, 84, 84, 0.16); color: #b23a3a; border-color: rgba(231, 84, 84, 0.35); }
.bg-tag-category { background: rgba(230, 255, 30, 0.2); color: #2a2d07; border-color: rgba(230, 255, 30, 0.46); }
.bg-tag-connection { background: rgba(230, 255, 30, 0.2); color: #2a2d07; border-color: rgba(230, 255, 30, 0.46); }
.bg-tag-platform { background: rgba(99, 117, 146, 0.14); color: #2f3b4f; border-color: rgba(99, 117, 146, 0.3); font-weight: 600; }

html[data-theme="dark"] .bg-tag-tier-a { color: #8be5bc; }
html[data-theme="dark"] .bg-tag-tier-b { color: #f2d28a; }
html[data-theme="dark"] .bg-tag-tier-c { color: #ffb6b6; }
html[data-theme="dark"] .bg-tag-category { color: #2a2d07; }
html[data-theme="dark"] .bg-tag-connection { color: #2a2d07; }
html[data-theme="dark"] .bg-tag-platform { color: #c5d1e8; }

.bg-card-actions {
  grid-area: buy;
  margin-top: 2px;
  display: flex;
  gap: 8px;
  flex-wrap: wrap;
  align-items: center;
}

.bg-card-details-toggle {
  display: inline-flex;
  align-items: center;
  justify-content: center;
  min-height: 36px;
  padding: 8px 12px;
  border: 1px solid var(--border);
  background: var(--card-solid);
  color: var(--text);
  border-radius: 10px;
  font-size: 0.84rem;
  font-weight: 700;
  cursor: pointer;
}

.bg-card-details-toggle:hover {
  border-color: var(--border-strong);
}

.bg-card-actions .bg-card-buy {
  margin: 0;
  padding: 0;
}

.bg-card-link a {
  display: inline-block;
  padding: 9px 14px;
  border: 1px solid var(--border);
  background: var(--card-solid);
  color: var(--text);
  border-radius: 10px;
  font-size: 0.88rem;
  font-weight: 700;
  text-decoration: none;
}

.bg-card-link a:hover {
  text-decoration: none;
  border-color: var(--border-strong);
}

.bg-card-buy a {
  display: inline-block;
  padding: 9px 14px;
  background: var(--cta);
  color: #2a2d07;
  border-radius: 10px;
  font-size: 0.88rem;
  font-weight: 700;
  text-decoration: none;
  letter-spacing: 0.01em;
  box-shadow: 0 8px 20px rgba(230, 255, 30, 0.28);
}

.bg-card-buy a:hover {
  color: #2a2d07;
  text-decoration: none;
  transform: translateY(-1px);
}

.bg-card-details {
  grid-area: details;
  width: 100%;
  border: 1px solid var(--border);
  border-radius: 12px;
  background: var(--panel);
  padding: 10px 10px 8px;
  margin-top: 2px;
}

.bg-card-details-header {
  display: flex;
  justify-content: space-between;
  align-items: center;
  gap: 10px;
  margin-bottom: 8px;
  font-size: 0.84rem;
  color: var(--muted);
  font-weight: 700;
  letter-spacing: 0.02em;
  text-transform: uppercase;
}

.bg-card-detail-link {
  font-size: 0.78rem;
  font-weight: 600;
  text-transform: none;
}

.bg-variant-list {
  display: flex;
  flex-direction: column;
  gap: 8px;
}

.bg-variant-row {
  border: 1px solid var(--border);
  border-radius: 10px;
  background: var(--card);
  padding: 8px 10px;
  display: flex;
  flex-direction: column;
  gap: 6px;
}

.bg-variant-head {
  display: flex;
  align-items: baseline;
  justify-content: space-between;
  gap: 8px;
  flex-wrap: wrap;
}

.bg-variant-mode {
  font-size: 0.9rem;
  color: var(--text);
  font-weight: 700;
}

.bg-variant-values {
  font-size: 0.88rem;
  font-weight: 700;
  color: var(--accent);
  white-space: nowrap;
}

.bg-variant-bar-track {
  position: relative;
  overflow: hidden;
  height: 10px;
  border-radius: 999px;
  border: 1px solid var(--border);
  background: rgba(99, 117, 146, 0.14);
}

.bg-variant-bar-fill {
  height: 100%;
  border-radius: 999px;
  min-width: 4px;
}

.bg-variant-meta {
  font-size: 0.82rem;
  color: var(--muted);
}

.dataTables_wrapper {
  overflow-x: auto;
  color: var(--text);
}

.dataTables_wrapper .dataTables_filter input,
.dataTables_wrapper .dataTables_length select {
  background: var(--card-solid);
  color: var(--text);
  border: 1px solid var(--border);
  border-radius: 8px;
}

.dataTables_wrapper .dataTables_info,
.dataTables_wrapper .dataTables_paginate {
  color: var(--muted) !important;
}

table.dataTable tbody tr {
  background: var(--table-row);
}

table.dataTable thead th,
table.dataTable tfoot th {
  color: var(--text);
}

.plotly {
  width: 100% !important;
}

.crosstalk-input-checkboxgroup label {
  margin-right: 14px;
  white-space: nowrap;
  color: var(--muted);
}

.bg-table-fallback {
  margin-top: 10px;
}

.bg-table-fallback summary {
  cursor: pointer;
  font-weight: 600;
  font-size: 1rem;
  color: var(--muted);
  padding: 8px 0;
}

.bg-inline-note {
  margin-top: 18px;
  color: var(--muted);
  font-size: 0.93rem;
}

.bg-controller-detail {
  margin: 12px 0 16px;
  padding: 14px 16px;
  border: 1px solid var(--border);
  border-radius: 14px;
  background: linear-gradient(135deg, var(--card) 0%, var(--panel) 100%);
}

.bg-controller-detail-head {
  display: grid;
  gap: 8px;
  align-items: center;
}

.bg-controller-detail-close {
  justify-self: start;
  min-height: 34px;
  padding: 7px 12px;
  border: 1px solid var(--border);
  border-radius: 10px;
  background: var(--card-solid);
  color: var(--text);
  font-weight: 700;
}

.bg-controller-detail-title {
  font-size: 1.35rem;
  line-height: 1.2;
  font-weight: 800;
  color: var(--text);
}

.bg-controller-detail-meta {
  font-size: 0.96rem;
  color: var(--muted);
}

.bg-controller-detail-actions {
  margin-top: 10px;
  display: flex;
  flex-wrap: wrap;
  gap: 8px;
}

.bg-controller-detail-actions a {
  display: inline-block;
  padding: 9px 13px;
  border: 1px solid var(--border);
  border-radius: 10px;
  text-decoration: none;
  font-weight: 700;
  color: var(--text);
  background: var(--card-solid);
}

.bg-controller-detail-actions a.bg-detail-raw {
  background: var(--cta);
  color: #2a2d07;
  border-color: rgba(230, 255, 30, 0.35);
}

.bg-controller-detail-body {
  margin-top: 12px;
}

.bg-compare-note {
  margin: 16px 0 8px;
  color: var(--muted);
  font-size: 0.9rem;
}

.bg-visual-compare-wrap {
  border: 1px solid var(--border);
  border-radius: 14px;
  padding: 10px;
  background: var(--panel);
}

small {
  color: var(--muted);
}

@media (max-width: 1200px) {
  .main-container {
    max-width: 98% !important;
  }
}

@media (min-width: 1020px) {
  .bg-filter-panel {
    position: sticky;
    top: 10px;
    z-index: 30;
  }
}

html[data-density="compact"] .bg-card-grid {
  gap: 10px;
}

html[data-density="compact"] .bg-card {
  padding: 12px 14px 11px;
  column-gap: 10px;
  row-gap: 6px;
}

html[data-density="compact"] .bg-card-name {
  font-size: 1.14rem;
}

html[data-density="compact"] .bg-card-metrics {
  font-size: 1.16rem;
}

html[data-density="compact"] .bg-tag {
  padding: 4px 10px;
  font-size: 0.82rem;
}

@media (max-width: 980px) {
  .bg-filter-controls {
    grid-template-columns: 1fr 1fr;
  }
}

@media (max-width: 760px) {
  div.tocify {
    position: relative !important;
    top: 0 !important;
    max-width: none !important;
  }

  .main-container {
    padding: 10px 12px 18px;
  }

  #header {
    border-radius: 16px;
    padding: 18px 15px;
  }

  .bg-card-grid {
    gap: 10px;
  }

  .bg-card {
    display: flex;
    flex-direction: column;
    align-items: stretch;
    gap: 8px;
    padding: 14px 12px 12px;
  }

  .bg-card-name {
    font-size: 1.22rem;
  }

  .bg-card-title {
    align-items: flex-start;
    flex-wrap: wrap;
  }

  .bg-card-metrics {
    text-align: left;
    font-size: 1.2rem;
  }

  .bg-card-actions {
    gap: 6px;
  }

  .bg-tag {
    font-size: 0.84rem;
  }

  .bg-filter-panel {
    padding: 16px 14px 14px;
    border-radius: 14px;
  }

  .bg-filter-controls {
    grid-template-columns: 1fr;
  }

  .bg-hero-actions {
    gap: 6px;
  }

  .bg-kpi-grid {
    grid-template-columns: 1fr 1fr;
  }

  .nav-tabs > li > a {
    padding: 9px 12px;
    font-size: 0.94rem;
  }
}

@media (prefers-reduced-motion: reduce) {
  * {
    animation-duration: 0.001ms !important;
    animation-iteration-count: 1 !important;
    transition-duration: 0.001ms !important;
    scroll-behavior: auto !important;
  }
}
</style>

```{r theme-bootstrap, echo=FALSE, results='asis'}
htmltools::HTML('
<script>
(function() {
  var THEME_KEY = "inputlatency-theme";
  var DENSITY_KEY = "inputlatency-density";
  var saved = null;
  try { saved = localStorage.getItem(THEME_KEY); } catch (e) {}
  var prefersDark = window.matchMedia && window.matchMedia("(prefers-color-scheme: dark)").matches;
  var theme = saved || (prefersDark ? "dark" : "light");
  document.documentElement.setAttribute("data-theme", theme);

  var density = "comfortable";
  try {
    var storedDensity = localStorage.getItem(DENSITY_KEY);
    if (storedDensity === "comfortable" || storedDensity === "compact") {
      density = storedDensity;
    }
  } catch (e) {}
  document.documentElement.setAttribute("data-density", density);
})();
</script>
')
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(gsheet)
library(DT)
library(crosstalk)
library(plotly)
library(htmlwidgets)

# Helper function to truncate long device names
truncate_name <- function(name, max_chars = 40) {
  ifelse(nchar(name) > max_chars,
         paste0(substr(name, 1, max_chars - 3), "..."),
         name)
}

normalize_device_name <- function(x) {
  x %>%
    tolower() %>%
    stringr::str_replace_all("&", " and ") %>%
    stringr::str_replace_all("[^a-z0-9]+", " ") %>%
    stringr::str_squish()
}

make_device_slug <- function(x) {
  normalize_device_name(x) %>%
    stringr::str_replace_all(" ", "-")
}

# Color palettes for consistent styling
connection_colors <- c(
  "Wired" = "#A8BE00",
  "Wireless" = "#5000DC"
)

category_colors <- c(
  "Arcade Stick" = "#5000DC",
  "Controller" = "#6A2DF0",
  "Adapter" = "#9BB000",
  "Arcade Encoder" = "#C6DD00",
  "Gamepad" = "#7D4DE2",
  "Flight Stick" = "#705600",
  "Racing Wheel" = "#2E215A",
  "Other" = "#7A8499"
)

wireless_type_colors <- c(
  "Bluetooth" = "#5000DC",
  "2.4 GHz" = "#A8BE00"
)
```

```{r load-gsheet-data, echo=FALSE, warning=FALSE}
sheet_url <- "https://docs.google.com/spreadsheets/d/1KlRObr3Be4zLch7Zyqg6qCJzGuhyGmXaOIUrpfncXIM/edit#gid=0"
cache_csv <- "../results/latency_sheet_cache.csv"
data_source <- "live"
data_source_label <- "Google Sheet (live)"
data_source_cached_at <- as.POSIXct(NA)
fetch_error <- NA_character_

dat_raw <- tryCatch({
  gsheet2tbl(sheet_url)
}, error = function(e) {
  fetch_error <<- conditionMessage(e)
  NULL
})

if (!is.null(dat_raw) && nrow(dat_raw) > 0) {
  write.csv(dat_raw, cache_csv, row.names = FALSE, na = "")
  if (file.exists(cache_csv)) {
    data_source_cached_at <- as.POSIXct(file.info(cache_csv)$mtime)
  }
} else if (file.exists(cache_csv)) {
  dat_raw <- read.csv(cache_csv, stringsAsFactors = FALSE, check.names = FALSE, na.strings = c("", "NA"))
  data_source <- "cache"
  data_source_label <- "Local cache (fallback)"
  data_source_cached_at <- as.POSIXct(file.info(cache_csv)$mtime)
  message("Using cached latency dataset from: ", format(data_source_cached_at, "%Y-%m-%d %H:%M %Z"))
} else {
  stop(
    "Unable to load data from Google Sheets and no cache file exists at ", cache_csv,
    ". Last error: ", fetch_error
  )
}

if (!"Latency Tier" %in% names(dat_raw) && "Tier" %in% names(dat_raw)) {
  dat_raw$`Latency Tier` <- dat_raw$Tier
}

# Ensure schema compatibility across sheet revisions / cache snapshots
required_cols <- c(
  "Make", "Model", "Device", "Link", "Connection", "Wired / Wireless",
  "Wireless Connection", "Home Button", "Latency Tier",
  "Average Measured Latency (in ms)",
  "Standard Deviation of Measured Latency (in ms)",
  "Max Measured Latency (in ms)",
  "Min Measured Latency (in ms)",
  "Category", "Face Buttons", "Date Added", "Valid Results"
)
for (col in required_cols) {
  if (!col %in% names(dat_raw)) {
    dat_raw[[col]] <- NA
  }
}

numeric_cols <- c(
  "Average Measured Latency (in ms)",
  "Standard Deviation of Measured Latency (in ms)",
  "Max Measured Latency (in ms)",
  "Min Measured Latency (in ms)"
)
for (col in intersect(numeric_cols, names(dat_raw))) {
  dat_raw[[col]] <- suppressWarnings(as.numeric(gsub("[^0-9.-]", "", dat_raw[[col]])))
}

dat <- dat_raw %>%
  mutate(Row = 2:(nrow(dat_raw) + 1)) %>%
  filter(toupper(as.character(`Valid Results`)) %in% c("YES", "TRUE", "1")) %>%
  select(
    Make, Model, Device, Link, Connection,
    "Wired/Wireless" = `Wired / Wireless`,
    "WirelessConnection" = `Wireless Connection`,
    `Home Button`,
    `Latency Tier`,
    "Latency (in ms)" = `Average Measured Latency (in ms)`,
    "SD" = `Standard Deviation of Measured Latency (in ms)`,
    "Max" = `Max Measured Latency (in ms)`,
    "Min" = `Min Measured Latency (in ms)`,
    Category, `Face Buttons`, Row, `Date Added`,
    Amazon = any_of("Amazon"),
    Price = any_of("Price"),
    any_of(c("MiSTer / PC", "Switch", "PS4", "PS5", "Xbox One", "Xbox Series"))
  ) %>%
  filter(!is.na(`Latency (in ms)`)) %>%
  arrange(`Latency (in ms)`) %>%
  mutate(
    ID = row_number(),
    DeviceClean = Device,
    DeviceNorm = normalize_device_name(DeviceClean),
    Device = ifelse(is.na(Link),
                    Device,
                    paste0('<a target=_blank href="', Link, '">', Device, '</a>'))
  ) %>%
  distinct(DeviceClean, Connection, .keep_all = TRUE) %>%
  arrange(`Latency (in ms)`)

# Build Platforms list-column from platform columns if they exist
platform_cols <- intersect(c("MiSTer / PC", "Switch", "PS4", "PS5", "Xbox One", "Xbox Series"), names(dat))
if (length(platform_cols) > 0) {
  dat$Platforms <- apply(dat[, platform_cols, drop = FALSE], 1, function(row) {
    cols <- platform_cols[!is.na(row) & trimws(toupper(row)) %in% c("YES", "TRUE", "X", "1")]
    paste(cols, collapse = ",")
  })
} else {
  dat$Platforms <- ""
}

# Clean Price column if it exists
if ("Price" %in% names(dat)) {
  dat$PriceNum <- as.numeric(gsub("[^0-9.]", "", dat$Price))
} else {
  dat$Price <- NA_character_
  dat$PriceNum <- NA_real_
}

# Ensure Amazon column exists
if (!"Amazon" %in% names(dat)) {
  dat$Amazon <- NA_character_
}

# Convert Excel serial dates to mm/dd/YYYY when needed (cache fallback compatibility)
if ("Date Added" %in% names(dat)) {
  serial_dates <- suppressWarnings(as.numeric(dat$`Date Added`))
  needs_serial_parse <- !is.na(serial_dates) & !grepl("/", dat$`Date Added`)
  if (any(needs_serial_parse, na.rm = TRUE)) {
    dat$`Date Added`[needs_serial_parse] <- format(
      as.Date(serial_dates[needs_serial_parse], origin = "1899-12-30"),
      "%m/%d/%Y"
    )
  }
}
```

```{r load-csv-data, echo=FALSE, warning=FALSE}
# Load raw CSV captures for detailed analysis
csv_dir <- "../captures/"
csv_files <- list.files(csv_dir, pattern = "\\.csv$", full.names = TRUE)

load_csv_with_device <- function(file_path) {
  device_name <- tools::file_path_sans_ext(basename(file_path))
  tryCatch({
    df <- read.csv(file_path, stringsAsFactors = FALSE)
    if (ncol(df) >= 2) {
      colnames(df)[1:2] <- c("read", "delay")
      df$Device <- device_name
      df <- df %>% select(Device, read, delay)
      return(df)
    }
    return(NULL)
  }, error = function(e) NULL)
}

raw_data <- lapply(csv_files, load_csv_with_device) %>%
  bind_rows() %>%
  filter(!is.na(delay)) %>%
  mutate(DeviceNorm = normalize_device_name(Device))

frame_ms <- 100 / 6

same_frame_from_samples <- function(delay_ms, frame_window_ms = frame_ms) {
  mean(pmax(0, 1 - delay_ms / frame_window_ms), na.rm = TRUE) * 100
}

same_frame_from_normal <- function(mu, sigma, frame_window_ms = frame_ms) {
  out <- rep(NA_real_, length(mu))

  valid <- !is.na(mu) & !is.na(sigma) & sigma > 0
  if (any(valid)) {
    z <- (frame_window_ms - mu[valid]) / sigma[valid]
    out[valid] <- (((frame_window_ms - mu[valid]) * pnorm(z)) + sigma[valid] * dnorm(z)) /
      frame_window_ms * 100
  }

  deterministic <- !is.na(mu) & (!is.na(sigma) & sigma <= 0)
  if (any(deterministic)) {
    out[deterministic] <- pmax(0, 1 - mu[deterministic] / frame_window_ms) * 100
  }

  fallback <- !is.na(mu) & is.na(out)
  if (any(fallback)) {
    out[fallback] <- pmax(0, 1 - mu[fallback] / frame_window_ms) * 100
  }

  out <- pmax(pmin(out, 100), 0)
  out
}

# Calculate percentile statistics from raw data
raw_stats <- raw_data %>%
  group_by(Device) %>%
  summarise(
    N = n(),
    RawMean = mean(delay, na.rm = TRUE),
    RawSD = sd(delay, na.rm = TRUE),
    Median = median(delay, na.rm = TRUE),
    P90 = quantile(delay, 0.90, na.rm = TRUE),
    P95 = quantile(delay, 0.95, na.rm = TRUE),
    P99 = quantile(delay, 0.99, na.rm = TRUE),
    IQR = IQR(delay, na.rm = TRUE),
    RawMin = min(delay, na.rm = TRUE),
    RawMax = max(delay, na.rm = TRUE),
    PctOnTime = round(same_frame_from_samples(delay), 1),
    BinA = round(sum(delay <= 100/6) / n() * 100, 1),
    BinB = round(sum(delay > 100/6 & delay <= 200/6) / n() * 100, 1),
    BinC = round(sum(delay > 200/6) / n() * 100, 1),
    .groups = 'drop'
  ) %>%
  mutate(Consistency = round(100 * (1 - RawSD / RawMean), 1))

if (nrow(raw_stats) > 0) {
  raw_device_index <- raw_stats %>%
    distinct(Device, RawMean) %>%
    arrange(RawMean, Device) %>%
    transmute(
      Device,
      DeviceNorm = normalize_device_name(Device)
    )
  raw_device_index$DeviceSlug <- make.unique(make_device_slug(raw_device_index$Device), sep = "-")
  raw_device_index$Tokens <- strsplit(raw_device_index$DeviceNorm, " ", fixed = TRUE)
} else {
  raw_device_index <- tibble::tibble(
    Device = character(0),
    DeviceNorm = character(0),
    DeviceSlug = character(0),
    Tokens = list()
  )
}

raw_stats_by_norm <- raw_data %>%
  group_by(DeviceNorm) %>%
  summarise(
    MatchedCaptureFiles = n_distinct(Device),
    N = n(),
    RawMean = mean(delay, na.rm = TRUE),
    RawSD = sd(delay, na.rm = TRUE),
    Median = median(delay, na.rm = TRUE),
    P90 = quantile(delay, 0.90, na.rm = TRUE),
    P95 = quantile(delay, 0.95, na.rm = TRUE),
    P99 = quantile(delay, 0.99, na.rm = TRUE),
    IQR = IQR(delay, na.rm = TRUE),
    RawMin = min(delay, na.rm = TRUE),
    RawMax = max(delay, na.rm = TRUE),
    PctOnTime = round(same_frame_from_samples(delay), 1),
    BinA = round(sum(delay <= 100/6) / n() * 100, 1),
    BinB = round(sum(delay > 100/6 & delay <= 200/6) / n() * 100, 1),
    BinC = round(sum(delay > 200/6) / n() * 100, 1),
    .groups = "drop"
  ) %>%
  mutate(Consistency = round(100 * (1 - RawSD / RawMean), 1))
```

```{r sd-imputation, echo=FALSE, warning=FALSE}
# SD imputation via linear regression (restored from backup)
dat$Device <- factor(dat$Device, levels = unique(dat$Device))
fit <- lm(data = dat, SD ~ `Latency (in ms)` + Min)
dat$Imputed <- is.na(dat$SD)
dat$SD[dat$Imputed] <- pmax(predict.lm(fit, dat[dat$Imputed, ]), 0.1)

dat <- dat %>%
  mutate(
    `SD up` = `Latency (in ms)` + qnorm(.975) * SD,
    `SD down` = pmax(`Latency (in ms)` - qnorm(.975) * SD, 0)
  )

# Merge raw stats where available (normalized name matching)
dat <- dat %>%
  left_join(raw_stats_by_norm, by = "DeviceNorm")

# Estimate PctOnTime/bins for devices without raw CSV data using normal distribution
missing <- is.na(dat$PctOnTime)
dat$PctOnTime[missing] <- round(
  same_frame_from_normal(dat$`Latency (in ms)`[missing], dat$SD[missing]),
  1
)
dat$BinA[missing] <- round(pnorm(100/6, dat$`Latency (in ms)`[missing], dat$SD[missing]) * 100, 1)
dat$BinB[missing] <- round(
  (pnorm(200/6, dat$`Latency (in ms)`[missing], dat$SD[missing]) -
   pnorm(100/6, dat$`Latency (in ms)`[missing], dat$SD[missing])) * 100, 1)
dat$BinC[missing] <- round(100 - dat$BinA[missing] - dat$BinB[missing], 1)
# Clamp negatives
dat$BinA <- pmax(dat$BinA, 0)
dat$BinB <- pmax(dat$BinB, 0)
dat$BinC <- pmax(dat$BinC, 0)

dat <- dat %>%
  mutate(
    HasRawCapture = !is.na(N),
    MetricSource = "Direct measurement"
  )

raw_unmatched <- raw_stats_by_norm %>%
  select(DeviceNorm, MatchedCaptureFiles) %>%
  left_join(
    raw_data %>% distinct(DeviceNorm, Device) %>% group_by(DeviceNorm) %>% summarise(
      CaptureExamples = paste(head(sort(unique(Device)), 3), collapse = "; "),
      .groups = "drop"
    ),
    by = "DeviceNorm"
  ) %>%
  anti_join(dat %>% distinct(DeviceNorm), by = "DeviceNorm") %>%
  arrange(desc(MatchedCaptureFiles), DeviceNorm)

sheet_without_raw <- dat %>%
  distinct(DeviceClean, DeviceNorm) %>%
  anti_join(raw_stats_by_norm %>% distinct(DeviceNorm), by = "DeviceNorm") %>%
  arrange(DeviceClean)

raw_coverage_pct <- ifelse(nrow(dat) > 0, round(mean(dat$HasRawCapture) * 100, 1), 0)

# Export derived datasets for maintenance workflows
write.csv(
  dat %>%
    mutate(
      `Latency (in ms)` = round(`Latency (in ms)`, 3),
      SD = round(SD, 3),
      PctOnTime = round(PctOnTime, 2)
    ),
  "../results/latency_cleaned_export.csv",
  row.names = FALSE,
  na = ""
)

write.csv(
  raw_unmatched,
  "../results/raw_capture_unmatched.csv",
  row.names = FALSE,
  na = ""
)

write.csv(
  sheet_without_raw,
  "../results/database_without_raw_capture.csv",
  row.names = FALSE,
  na = ""
)
```

# MiSTer Controller Latency Database {.tabset .tabset-fade}

You can find the full spreadsheet [here](https://docs.google.com/spreadsheets/d/1KlRObr3Be4zLch7Zyqg6qCJzGuhyGmXaOIUrpfncXIM/edit#gid=0). Store links are often affiliate.

```{r data-source-status, echo=FALSE, results='asis'}
cache_txt <- if (!is.na(data_source_cached_at)) {
  format(data_source_cached_at, "%Y-%m-%d %H:%M %Z")
} else {
  "not cached yet"
}

cat(sprintf(
  '<div class="bg-source-note"><strong>Data source:</strong> %s. <strong>Last cache write:</strong> %s.</div>',
  data_source_label,
  cache_txt
))
```

```{r hero-summary, echo=FALSE}
source_short <- ifelse(data_source == "live", "Live Sheet", "Cache Fallback")
buyers_guide_group_count <- dat %>%
  mutate(
    GroupName = stringr::str_squish(paste(Make, Model)),
    GroupName = if_else(is.na(GroupName) | GroupName == "", DeviceClean, GroupName),
    GroupKey = normalize_device_name(paste(GroupName, `Wired/Wireless`, Category))
  ) %>%
  distinct(GroupKey) %>%
  nrow()

h <- c(
  '<section class="bg-hero">',
  '<div class="bg-hero-title">Fast, searchable controller latency intelligence</div>',
  '<p class="bg-hero-sub">Filter by platform and connection, compare on-time behavior, and drill into raw-capture quality in one workflow.</p>',
  '<div class="bg-hero-actions">',
  "<a class=\"bg-hero-btn\" href=\"#buyers-guide\" onclick=\"return openTabSection('buyers-guide');\">Buyer's Guide</a>",
  '<a class="bg-hero-btn" href="#detailed-analysis" onclick="return openTabSection(\'detailed-analysis\');">Detailed Analysis</a>',
  '<a class="bg-hero-btn" href="#raw-data-deep-dive" onclick="return openTabSection(\'raw-data-deep-dive\');">Raw Data Deep Dive</a>',
  '</div>',
  '<div class="bg-hero-meta">',
  sprintf('<span>%d device groups in buyer view</span>', buyers_guide_group_count),
  sprintf('<span>%d mode results tracked</span>', nrow(dat)),
  sprintf('<span>%.1f%% raw capture coverage</span>', raw_coverage_pct),
  sprintf('<span>Data source: %s</span>', source_short),
  '</div>',
  '</section>'
)
htmltools::HTML(paste(h, collapse = "\n"))
```

## Buyer's Guide

Find the right controller for your setup. Filter by category, connection type, and platform, then browse results ranked by latency.

```{r buyers-guide-kpis, echo=FALSE}
under_one_frame <- sum(dat$`Latency (in ms)` < 100/6, na.rm = TRUE)
wireless_count <- sum(dat$`Wired/Wireless` == "Wireless", na.rm = TRUE)

h <- c(
  '<div class="bg-kpi-grid">',
  sprintf('<div class="bg-kpi"><div class="label">Device Groups</div><div class="value">%d</div></div>', buyers_guide_group_count),
  sprintf('<div class="bg-kpi"><div class="label">Under 1 Frame</div><div class="value">%d</div></div>', under_one_frame),
  sprintf('<div class="bg-kpi"><div class="label">Wireless Tested</div><div class="value">%d</div></div>', wireless_count),
  sprintf('<div class="bg-kpi"><div class="label">Raw Capture Coverage</div><div class="value">%.1f%%</div></div>', raw_coverage_pct),
  '</div>'
)

htmltools::HTML(paste(h, collapse = "\n"))
```

```{r buyers-guide-recent, echo=FALSE, warning=FALSE}
# ── Recently Added strip ──────────────────────────────────
recent <- dat %>%
  mutate(DateParsed = as.Date(`Date Added`, format = "%m/%d/%Y")) %>%
  filter(!is.na(DateParsed)) %>%
  arrange(desc(DateParsed)) %>%
  slice_head(n = 8)

if (nrow(recent) > 0) {
  h <- c('<h4 style="margin-bottom:12px;">Recently Added</h4>',
         '<div class="bg-recent-strip">')
  for (i in seq_len(nrow(recent))) {
    r <- recent[i, ]
    lat <- round(r$`Latency (in ms)`, 2)
    tier_class <- if (lat < 100/6) "bg-tag-tier-a" else if (lat < 200/6) "bg-tag-tier-b" else "bg-tag-tier-c"
    h <- c(h, sprintf('<div class="bg-recent-chip"><span class="chip-badge %s">%.2f ms</span> %s</div>',
                       tier_class, lat, htmltools::htmlEscape(r$DeviceClean)))
  }
  h <- c(h, '</div>')
  htmltools::HTML(paste(h, collapse = "\n"))
}
```

```{r buyers-guide-filters, echo=FALSE, warning=FALSE}
# ── Filter panel ──────────────────────────────────────────
categories <- sort(unique(na.omit(dat$Category)))
connections <- sort(unique(na.omit(dat$`Wired/Wireless`)))
unique_non_empty <- function(x) {
  v <- as.character(x)
  v <- stringr::str_squish(v)
  v <- v[!is.na(v) & nzchar(v) & v != "-" & tolower(v) != "na" & tolower(v) != "n/a"]
  sort(unique(v))
}
normalize_face_buttons_value <- function(x) {
  v <- stringr::str_squish(as.character(x))
  num <- suppressWarnings(as.numeric(v))
  whole <- !is.na(num) & abs(num - round(num)) < 1e-9
  v[whole] <- as.character(as.integer(round(num[whole])))
  v
}
face_button_values <- unique_non_empty(dat$`Face Buttons`)
face_button_values <- sort(unique(normalize_face_buttons_value(face_button_values)))
home_button_values <- unique_non_empty(dat$`Home Button`)

infer_analog_capability <- function(make, model, device_clean, category) {
  category_txt <- tolower(stringr::str_squish(as.character(category)))
  if (category_txt == "controller adapter") return("Depends on controller")
  if (category_txt %in% c("joystick", "joystick encoder")) return("No analog sticks")

  text <- tolower(stringr::str_squish(paste(make, model, device_clean, category)))
  yes_rx <- paste(
    "dualsense", "dualshock", "xbox", "switch\\s*pro", "wii\\s*u\\s*pro",
    "pro\\s*2", "elite", "pro\\s*controller", "f310", "f710",
    "wireless\\s+controller", "horipad", "brawlergen", sep = "|"
  )
  no_rx <- paste(
    "fighting\\s+commander", "fightpad", "fighting\\s+stick", "arcade\\s+stick",
    "classic", "nes", "snes", "genesis", "saturn", "neo-?geo", "pc\\s*engine",
    "6\\s*button", "astro\\s*city", "wii\\s*classic", sep = "|"
  )

  if (grepl(yes_rx, text, perl = TRUE)) return("Has analog sticks")
  if (grepl(no_rx, text, perl = TRUE)) return("No analog sticks")
  "Unknown"
}

preferred_analog_cols <- c(
  "Analog Axes", "Analog Axis", "Analog Sticks", "Analog Sticks Count",
  "Analog", "Analog Joysticks", "Analog Sticks?"
)
dat_col_names <- names(dat)
dat_col_names_lc <- tolower(dat_col_names)
preferred_hits <- match(tolower(preferred_analog_cols), dat_col_names_lc, nomatch = 0)
preferred_hits <- preferred_hits[preferred_hits > 0]
regex_hits <- which(grepl("analog|thumb\\s*stick|sticks?\\b|axes?\\b", dat_col_names_lc))
analog_axis_hits <- unique(c(preferred_hits, regex_hits))
analog_axis_col <- if (length(analog_axis_hits) > 0) dat_col_names[analog_axis_hits[[1]]] else NA_character_

if (is.na(analog_axis_col)) {
  dat$`Analog Joysticks` <- mapply(
    infer_analog_capability,
    dat$Make,
    dat$Model,
    dat$DeviceClean,
    dat$Category,
    USE.NAMES = FALSE
  )
  analog_axis_col <- "Analog Joysticks"
}

analog_axis_values <- if (!is.na(analog_axis_col)) unique_non_empty(dat[[analog_axis_col]]) else character(0)
if (identical(analog_axis_col, "Analog Joysticks") && length(analog_axis_values) > 0) {
  analog_pref <- c("Has analog sticks", "No analog sticks", "Depends on controller", "Unknown")
  analog_axis_values <- analog_axis_values[order(match(analog_axis_values, analog_pref), analog_axis_values, na.last = TRUE)]
}

# Derive available platforms
all_platforms <- c("MiSTer / PC", "Switch", "PS4", "PS5", "Xbox One", "Xbox Series")
avail_platforms <- intersect(all_platforms, platform_cols)

h <- c(
  '<div class="bg-filter-panel">',
  '<div class="bg-filter-controls">',
  '<div class="bg-filter-search"><input type="search" id="bg-search" placeholder="Search device, brand, category..." aria-label="Search devices"></div>',
  '<div class="bg-filter-sort"><select id="bg-sort" aria-label="Sort devices">',
  '<option value="latency_asc">Sort: Lowest latency</option>',
  '<option value="latency_desc">Sort: Highest latency</option>',
  '<option value="ontime_desc">Sort: Highest same-frame probability</option>',
  '<option value="price_asc">Sort: Lowest price</option>',
  '</select></div>',
  '<button class="bg-density-btn" type="button" id="density-toggle" onclick="toggleDensity()">Density</button>',
  '<button class="bg-theme-btn" type="button" id="theme-toggle" onclick="toggleTheme()">Theme</button>',
  '<button class="bg-reset-btn" type="button" id="bg-reset" onclick="resetFilters()">Reset</button>',
  '</div>'
)

# Wired/Wireless row
h <- c(h, '<div class="bg-filter-group"><h4>Wired/Wireless</h4>',
       '<button class="filter-btn active" data-dim="connection" data-val="all" onclick="toggleFilter(\'connection\',\'all\',this)">All</button>')
for (conn in connections) {
  esc <- htmltools::htmlEscape(conn)
  h <- c(h, sprintf('<button class="filter-btn" data-dim="connection" data-val="%s" onclick="toggleFilter(\'connection\',\'%s\',this)">%s</button>',
                    esc, esc, esc))
}
h <- c(h, '</div>')

# Home button row
h <- c(h, '<div class="bg-filter-group"><h4>Home Button</h4>',
       '<button class="filter-btn active" data-dim="home" data-val="all" onclick="toggleFilter(\'home\',\'all\',this)">All</button>')
for (val in home_button_values) {
  esc <- htmltools::htmlEscape(val)
  h <- c(h, sprintf('<button class="filter-btn" data-dim="home" data-val="%s" onclick="toggleFilter(\'home\',\'%s\',this)">%s</button>',
                    esc, esc, esc))
}
h <- c(h, '</div>')

# Face button row
h <- c(h, '<div class="bg-filter-group"><h4>Face Buttons</h4>',
       '<button class="filter-btn active" data-dim="face" data-val="all" onclick="toggleFilter(\'face\',\'all\',this)">All</button>')
for (val in face_button_values) {
  esc <- htmltools::htmlEscape(val)
  h <- c(h, sprintf('<button class="filter-btn" data-dim="face" data-val="%s" onclick="toggleFilter(\'face\',\'%s\',this)">%s</button>',
                    esc, esc, esc))
}
h <- c(h, '</div>')

# Category row
h <- c(h, '<div class="bg-filter-group"><h4>Category</h4>',
       '<button class="filter-btn active" data-dim="category" data-val="all" onclick="toggleFilter(\'category\',\'all\',this)">All</button>')
for (cat_name in categories) {
  esc <- htmltools::htmlEscape(cat_name)
  h <- c(h, sprintf('<button class="filter-btn" data-dim="category" data-val="%s" onclick="toggleFilter(\'category\',\'%s\',this)">%s</button>',
                    esc, esc, esc))
}
h <- c(h, '</div>')

h <- c(h, '</div>',  # close filter panel
       '<div class="bg-counter" id="bg-counter"></div>',
       '<div class="bg-counter" id="bg-match-counter"></div>')

htmltools::HTML(paste(h, collapse = "\n"))
```

```{r buyers-guide-cards, echo=FALSE, warning=FALSE}
# ── Result cards (grouped by controller mode) ───────────────────────────────
frame_ms <- 100 / 6

fmt_pct_label <- function(pct) {
  if (abs(pct - round(pct)) < 0.05) sprintf("%.0f%%", round(pct)) else sprintf("%.1f%%", pct)
}

extract_mode_from_name <- function(x) {
  m <- stringr::str_match(x, "\\[(.+?)\\]")[, 2]
  ifelse(is.na(m), "", m)
}

is_generic_mode <- function(x) {
  x <- tolower(stringr::str_squish(as.character(x)))
  if (!nzchar(x) || x %in% c("-", "?", "n/a", "na", "none", "default")) {
    return(TRUE)
  }

  generic_patterns <- c(
    "^wired$",
    "^wireless$",
    "^wired usb$",
    "^wired usb c$",
    "^wired usb a$",
    "^wireless usb$",
    "^usb$",
    "^usb c$",
    "^usb a$",
    "^wired connection$",
    "^wireless connection$"
  )

  any(stringr::str_detect(x, generic_patterns))
}

pick_mode_label <- function(mode_from_name, connection, wireless_connection) {
  candidates <- c(mode_from_name, connection, wireless_connection)
  candidates <- stringr::str_squish(as.character(candidates))
  candidates <- candidates[!is.na(candidates) & nzchar(candidates)]
  if (length(candidates) == 0) return("")

  non_generic <- candidates[!vapply(candidates, is_generic_mode, logical(1))]
  if (length(non_generic) == 0) "" else non_generic[[1]]
}

collapse_platforms <- function(x) {
  raw <- paste(x[!is.na(x) & nzchar(trimws(x))], collapse = ",")
  if (!nzchar(raw)) return("")
  vals <- trimws(unlist(strsplit(raw, ",")))
  vals <- vals[nzchar(vals)]
  paste(sort(unique(vals)), collapse = ",")
}

safe_text <- function(x, fallback = "") {
  v <- as.character(x)
  v <- v[!is.na(v) & nzchar(trimws(v))]
  if (length(v) == 0) fallback else trimws(v[[1]])
}

collapse_distinct_values <- function(x) {
  vals <- stringr::str_squish(as.character(x))
  vals <- vals[!is.na(vals) & nzchar(vals) & vals != "-" & tolower(vals) != "na" & tolower(vals) != "n/a"]
  unique(vals)
}
if (!exists("analog_axis_col")) {
  analog_axis_col <- NA_character_
}

tokenize_for_match <- function(x) {
  out <- unlist(strsplit(normalize_device_name(x), " ", fixed = TRUE))
  out <- out[nzchar(out)]
  unique(out)
}

match_drop_tokens <- c(
  "controller", "gamepad", "adapter", "converter", "cable",
  "for", "the", "and", "to", "wired", "wireless", "usb",
  "mode", "input", "xinput", "dinput", "windows", "switch",
  "playstation", "xbox", "pc", "series", "model"
)

find_raw_device_for_group <- function(group_df) {
  if (!exists("raw_device_index") || nrow(raw_device_index) == 0) {
    return(list(Device = NA_character_, Slug = NA_character_))
  }

  group_norms <- unique(group_df$DeviceNorm)
  group_norms <- group_norms[!is.na(group_norms) & nzchar(trimws(group_norms))]
  exact_hits <- raw_device_index %>% filter(DeviceNorm %in% group_norms)
  if (nrow(exact_hits) > 0) {
    return(list(Device = exact_hits$Device[[1]], Slug = exact_hits$DeviceSlug[[1]]))
  }

  group_make <- safe_text(group_df$Make, "")
  group_model <- safe_text(group_df$Model, "")
  group_name <- safe_text(group_df$GroupName, safe_text(group_df$DeviceClean, ""))
  group_category <- tolower(safe_text(group_df$Category, ""))

  make_tokens <- tokenize_for_match(group_make)
  model_source <- if (nzchar(group_model)) group_model else group_name
  model_tokens <- tokenize_for_match(model_source)
  if (length(make_tokens) > 0) {
    model_tokens <- setdiff(model_tokens, make_tokens)
  }
  model_tokens <- setdiff(model_tokens, match_drop_tokens)
  if (length(model_tokens) == 0) {
    model_tokens <- setdiff(tokenize_for_match(group_name), c(make_tokens, match_drop_tokens))
  }
  if (length(model_tokens) == 0) {
    return(list(Device = NA_character_, Slug = NA_character_))
  }

  raw_tokens <- raw_device_index$Tokens
  make_match <- if (length(make_tokens) == 0) {
    rep(TRUE, nrow(raw_device_index))
  } else {
    vapply(raw_tokens, function(tok) any(tok %in% make_tokens), logical(1))
  }
  overlap <- vapply(raw_tokens, function(tok) sum(model_tokens %in% tok), integer(1))
  denom <- max(length(unique(model_tokens)), 1L)
  score <- overlap / denom

  # Avoid mapping controller rows to obvious adapter/encoder captures.
  raw_is_adapter <- stringr::str_detect(raw_device_index$DeviceNorm, "\\b(adapter|converter|encoder)\\b")
  group_is_adapter <- stringr::str_detect(group_category, "adapter|encoder")
  if (!group_is_adapter) {
    score[raw_is_adapter] <- pmax(score[raw_is_adapter] - 0.35, 0)
  }

  score[!make_match] <- 0
  best_idx <- which.max(score)
  if (!length(best_idx) || score[[best_idx]] < 0.7 || overlap[[best_idx]] < 2) {
    return(list(Device = NA_character_, Slug = NA_character_))
  }

  list(
    Device = raw_device_index$Device[[best_idx]],
    Slug = raw_device_index$DeviceSlug[[best_idx]]
  )
}

card_variants <- dat %>%
  mutate(
    GroupName = stringr::str_squish(paste(Make, Model)),
    GroupName = if_else(is.na(GroupName) | GroupName == "", DeviceClean, GroupName),
    ModeFromName = extract_mode_from_name(DeviceClean),
    ModeLabel = purrr::pmap_chr(
      list(ModeFromName, Connection, WirelessConnection),
      pick_mode_label
    ),
    GroupKey = normalize_device_name(paste(GroupName, `Wired/Wireless`, Category)),
    PctOnTimeSafe = pmax(
      0,
      pmin(
        ifelse(
          is.na(PctOnTime),
          pmax(0, (1 - (`Latency (in ms)` / frame_ms)) * 100),
          PctOnTime
        ),
        99.9
      )
    )
  )

group_splits <- split(card_variants, card_variants$GroupKey)
group_order <- names(sort(vapply(
  group_splits,
  function(g) min(g$`Latency (in ms)`, na.rm = TRUE),
  numeric(1)
)))
group_slug_map <- stats::setNames(make.unique(make_device_slug(group_order), sep = "-"), group_order)
scatter_rows <- list()

h <- c(
  '<section class="bg-controller-detail" id="bg-controller-detail" hidden>',
  '<div class="bg-controller-detail-head">',
  '<button class="bg-controller-detail-close" type="button" onclick="closeControllerPage()">Back to list</button>',
  '<div class="bg-controller-detail-title" id="bg-controller-detail-title"></div>',
  '<div class="bg-controller-detail-meta" id="bg-controller-detail-meta"></div>',
  '</div>',
  '<div class="bg-controller-detail-actions" id="bg-controller-detail-actions"></div>',
  '<div class="bg-controller-detail-body" id="bg-controller-detail-body"></div>',
  '</section>',
  '<div class="bg-card-grid" id="bg-card-grid">'
)

for (rank_idx in seq_along(group_order)) {
  key <- group_order[[rank_idx]]
  controller_slug <- group_slug_map[[key]]
  g <- group_splits[[key]] %>%
    arrange(`Latency (in ms)`, DeviceClean)
  d <- g[1, ]

  lat <- round(d$`Latency (in ms)`, 2)
  pct_ontime <- max(min(d$PctOnTimeSafe, 99.9), 0)
  ontime_label <- fmt_pct_label(pct_ontime)
  meter_color <- if (pct_ontime >= 90) "#24a86b" else if (pct_ontime >= 75) "#A8BE00" else if (pct_ontime >= 50) "#d98d2b" else "#d95656"

  cat_val <- safe_text(d$Category)
  conn_val <- safe_text(d$`Wired/Wireless`)
  platforms_str <- collapse_platforms(g$Platforms)
  group_name <- safe_text(d$GroupName, d$DeviceClean)
  best_mode <- safe_text(d$ModeLabel, "")
  mode_values <- as.character(g$ModeLabel)
  mode_values <- mode_values[!is.na(mode_values)]
  mode_values <- unique(stringr::str_squish(mode_values))
  mode_values <- mode_values[nzchar(mode_values)]
  mode_count <- length(mode_values)
  mode_line <- if (mode_count > 1 && nzchar(best_mode)) {
    sprintf("Best mode: %s (%d modes tested)", best_mode, mode_count)
  } else if (mode_count > 1) {
    sprintf("%d modes tested", mode_count)
  } else if (mode_count == 1) {
    sprintf("Mode: %s", mode_values[[1]])
  } else {
    ""
  }

  face_values <- collapse_distinct_values(g$`Face Buttons`)
  if (length(face_values) > 0) {
    face_values <- unique(normalize_face_buttons_value(face_values))
  }
  home_values <- collapse_distinct_values(g$`Home Button`)
  analog_values <- if (!is.na(analog_axis_col) && analog_axis_col %in% names(g)) {
    collapse_distinct_values(g[[analog_axis_col]])
  } else {
    character(0)
  }
  face_attr <- paste(face_values, collapse = "|")
  home_attr <- paste(home_values, collapse = "|")
  analog_attr <- paste(analog_values, collapse = "|")
  face_label <- if (length(face_values) > 0) face_values[[1]] else ""
  home_label <- if (length(home_values) > 0) home_values[[1]] else ""
  analog_label <- if (length(analog_values) > 0) analog_values[[1]] else ""

  # Pick first available buy link among fastest variants.
  buy_url <- NA_character_
  controller_url <- NA_character_
  for (j in seq_len(nrow(g))) {
    amazon_j <- safe_text(g$Amazon[j], "")
    link_j <- safe_text(g$Link[j], "")
    if (is.na(controller_url) && nzchar(link_j)) {
      controller_url <- link_j
    }
    candidate <- if (nzchar(amazon_j)) amazon_j else if (nzchar(link_j)) link_j else ""
    if (nzchar(candidate)) {
      buy_url <- candidate
      break
    }
  }
  if (is.na(controller_url) && !is.na(buy_url) && nzchar(trimws(buy_url))) {
    controller_url <- buy_url
  }
  if (is.na(controller_url) || !nzchar(trimws(controller_url))) {
    query <- stringr::str_squish(paste(group_name, "controller"))
    if (nzchar(query)) {
      controller_url <- paste0("https://duckduckgo.com/?q=", utils::URLencode(query, reserved = TRUE))
    }
  }

  valid_prices <- suppressWarnings(as.numeric(g$PriceNum))
  valid_prices <- valid_prices[is.finite(valid_prices) & valid_prices > 0]
  price_num <- if (length(valid_prices) > 0) min(valid_prices) else NA_real_
  price_attr <- ifelse(is.na(price_num), "", sprintf("%.2f", price_num))

  search_parts <- unique(c(
    g$DeviceClean, g$ModeLabel, g$Connection, g$WirelessConnection,
    g$Category, g$`Wired/Wireless`, g$Platforms, g$Make, g$Model,
    face_values, home_values, analog_values
  ))
  search_parts <- search_parts[!is.na(search_parts) & nzchar(trimws(search_parts))]
  search_blob <- tolower(paste(search_parts, collapse = " "))

  conn_badge_html <- if (nzchar(conn_val)) {
    sprintf(
      '<span class="bg-tag bg-tag-connection bg-card-connection-badge">%s</span>',
      htmltools::htmlEscape(conn_val)
    )
  } else {
    ""
  }

  buy_html <- if (!is.na(buy_url) && nzchar(trimws(buy_url))) {
    sprintf('<div class="bg-card-buy"><a href="%s" target="_blank">Buy &rarr;</a></div>',
            htmltools::htmlEscape(buy_url))
  } else {
    ""
  }

  controller_html <- if (!is.na(controller_url) && nzchar(trimws(controller_url))) {
    sprintf('<div class="bg-card-link"><a href="%s" target="_blank">Controller &uarr;</a></div>',
            htmltools::htmlEscape(controller_url))
  } else {
    ""
  }

  raw_match <- find_raw_device_for_group(g)
  raw_device_slug <- safe_text(raw_match$Slug, "")
  has_distribution <- nzchar(raw_device_slug)
  raw_target_text <- if (has_distribution) "Open Raw Distribution" else "Open Raw Deep Dive"
  raw_target_href <- if (has_distribution) {
    sprintf("#raw-dist-%s", raw_device_slug)
  } else {
    "#raw-data-deep-dive"
  }
  raw_target_onclick <- if (has_distribution) {
    sprintf("return openRawDistribution('%s');", raw_device_slug)
  } else {
    "return openTabSection('raw-data-deep-dive');"
  }

  open_page_btn <- sprintf(
    '<button class="bg-card-details-toggle" type="button" onclick="return openControllerPage(\'%s\');">Open page</button>',
    controller_slug
  )
  actions_html <- sprintf(
    '<div class="bg-card-actions">%s%s%s</div>',
    open_page_btn,
    controller_html,
    buy_html
  )

  detail_rows <- c(
    '<div class="bg-card-details">',
    '<div class="bg-card-details-header"><span>Mode-By-Mode Results</span></div>',
    '<div class="bg-variant-list">'
  )

  for (j in seq_len(nrow(g))) {
    v <- g[j, ]
    v_mode <- safe_text(v$ModeLabel, "")
    if (!nzchar(v_mode)) {
      v_wireless <- safe_text(v$WirelessConnection, "")
      v_mode <- if (nzchar(v_wireless) && !is_generic_mode(v_wireless)) v_wireless else "Measured result"
    }
    v_lat <- round(v$`Latency (in ms)`, 2)
    v_pct <- max(min(v$PctOnTimeSafe, 99.9), 0)
    v_sd <- if (!is.na(v$SD)) sprintf("SD %.2f", as.numeric(v$SD)) else "SD n/a"
    v_conn <- safe_text(v$Connection)
    if (tolower(v_conn) == tolower(v_mode) || is_generic_mode(v_conn)) {
      v_conn <- ""
    }
    v_platform <- safe_text(v$Platforms)
    meta_parts <- unique(c(v_conn, v_platform, v_sd))
    meta_parts <- meta_parts[nzchar(meta_parts)]
    v_meta <- paste(meta_parts, collapse = " | ")
    bar_width <- max(0, min(100, v_pct))
    bar_color <- if (v_pct >= 90) "#24a86b" else if (v_pct >= 75) "#A8BE00" else if (v_pct >= 50) "#d98d2b" else "#d95656"

    detail_rows <- c(detail_rows, sprintf(
      '<div class="bg-variant-row"><div class="bg-variant-head"><div class="bg-variant-mode">%s</div><div class="bg-variant-values">%.2fms<span class="bg-metric-sep">|</span>%s Same-Frame</div></div><div class="bg-variant-bar-track"><div class="bg-variant-bar-fill" style="width:%.1f%%;background:%s;"></div></div><div class="bg-variant-meta">%s</div></div>',
      htmltools::htmlEscape(v_mode),
      v_lat,
      fmt_pct_label(v_pct),
      bar_width,
      bar_color,
      htmltools::htmlEscape(v_meta)
    ))
  }

  detail_rows <- c(detail_rows, '</div></div>')
  details_html <- paste(detail_rows, collapse = "")
  details_template_html <- sprintf(
    '<template id="bg-controller-template-%s">%s</template>',
    controller_slug,
    details_html
  )
  card_anchor_html <- sprintf('<span class="bg-controller-anchor" id="controller-%s" hidden></span>', controller_slug)

  meter_html <- sprintf(
    '<div class="bg-card-probability"><div class="bg-prob-track"><div class="bg-prob-fill" style="width:%.1f%%;background:%s;"></div></div></div>',
    pct_ontime,
    meter_color
  )

  scatter_rows[[length(scatter_rows) + 1]] <- tibble::tibble(
    Slug = controller_slug,
    Device = group_name,
    Connection = conn_val,
    Category = cat_val,
    Latency = lat,
    SameFrame = pct_ontime,
    SD = suppressWarnings(as.numeric(d$SD)),
    RawSlug = raw_device_slug
  )

  h <- c(h, sprintf(
    '<div class="bg-card" data-controller-slug="%s" data-category="%s" data-connection="%s" data-platforms="%s" data-search="%s" data-latency="%.3f" data-ontime="%.3f" data-price="%s" data-face="%s" data-home="%s" data-analog="%s" data-controller-url="%s" data-buy-url="%s" data-raw-slug="%s" data-raw-target-href="%s" data-raw-target-onclick="%s" data-raw-target-text="%s">
<div class="bg-card-rank">#%d</div>
<div class="bg-card-title"><div class="bg-card-name">%s</div>%s</div>
<div class="bg-card-metrics">%.2fms<span class="bg-metric-sep">|</span>%s Same-Frame</div>
%s
%s
%s
%s
%s
%s%s%s
</div>',
    htmltools::htmlEscape(controller_slug),
    htmltools::htmlEscape(cat_val),
    htmltools::htmlEscape(conn_val),
    htmltools::htmlEscape(platforms_str),
    htmltools::htmlEscape(search_blob),
    lat,
    pct_ontime,
    price_attr,
    htmltools::htmlEscape(face_attr),
    htmltools::htmlEscape(home_attr),
    htmltools::htmlEscape(analog_attr),
    htmltools::htmlEscape(safe_text(controller_url, "")),
    htmltools::htmlEscape(safe_text(buy_url, "")),
    htmltools::htmlEscape(raw_device_slug),
    htmltools::htmlEscape(raw_target_href),
    htmltools::htmlEscape(raw_target_onclick),
    htmltools::htmlEscape(raw_target_text),
    rank_idx,
    htmltools::htmlEscape(group_name),
    conn_badge_html,
    lat,
    ontime_label,
    if (nzchar(face_label)) sprintf('<div class="bg-card-mode">Face Buttons: %s</div>', htmltools::htmlEscape(face_label)) else "",
    if (nzchar(home_label)) sprintf('<div class="bg-card-mode">Home Button: %s</div>', htmltools::htmlEscape(home_label)) else "",
    if (nzchar(analog_label) && !is.na(analog_axis_col)) sprintf('<div class="bg-card-mode">%s: %s</div>', htmltools::htmlEscape(analog_axis_col), htmltools::htmlEscape(analog_label)) else "",
    if (nzchar(mode_line)) sprintf('<div class="bg-card-mode">%s</div>', htmltools::htmlEscape(mode_line)) else "",
    meter_html,
    actions_html,
    card_anchor_html,
    details_template_html
  ))
}

h <- c(h, '</div>')  # close card grid
buyers_scatter_dat <- dplyr::bind_rows(scatter_rows)

htmltools::HTML(paste(h, collapse = "\n"))
```

<p class="bg-inline-note">Use <strong>Open page</strong> on any card for a shopper-focused controller profile, then jump directly to raw distribution when available.</p>

```{r buyers-guide-scatter, echo=FALSE, warning=FALSE}
if (exists("buyers_scatter_dat") && nrow(buyers_scatter_dat) > 0) {
  scatter_df <- buyers_scatter_dat %>%
    mutate(
      SD = ifelse(is.na(SD), median(SD, na.rm = TRUE), SD),
      SD = ifelse(is.finite(SD), SD, 0.1),
      SameFrameLabel = ifelse(
        abs(SameFrame - round(SameFrame)) < 0.05,
        sprintf("%.0f%%", round(SameFrame)),
        sprintf("%.1f%%", SameFrame)
      ),
      HoverText = paste0(
        Device, "<br>",
        sprintf("Latency: %.2f ms", Latency), "<br>",
        sprintf("Same-frame: %s", SameFrameLabel), "<br>",
        "Connection: ", Connection, "<br>",
        "Category: ", Category
      )
    )

  p_buyer_scatter <- plot_ly(
    data = scatter_df,
    x = ~Latency,
    y = ~SameFrame,
    type = "scatter",
    mode = "markers",
    customdata = ~Slug,
    text = ~HoverText,
    hoverinfo = "text",
    color = ~Connection,
    colors = c("Wired" = "#A8BE00", "Wireless" = "#5000DC"),
    symbol = ~Category,
    symbols = c("circle", "diamond", "square", "triangle-up"),
    marker = list(
      sizemode = "diameter",
      sizeref = 0.4,
      line = list(width = 1, color = "rgba(16,22,34,0.35)")
    ),
    size = ~pmax(SD, 0.1)
  ) %>%
    layout(
      title = list(text = "Visual Compare: Wired vs Wireless", x = 0.02),
      xaxis = list(title = "Average Latency (ms)"),
      yaxis = list(title = "Same-Frame Probability (%)", range = c(0, 100)),
      legend = list(orientation = "h", x = 0, y = 1.1),
      margin = list(t = 70, r = 20, b = 55, l = 70),
      hovermode = "closest",
      height = 460
    ) %>%
    htmlwidgets::onRender(
      "function(el, x) {
        el.on('plotly_click', function(evt) {
          if (!evt || !evt.points || !evt.points.length) return;
          var slug = evt.points[0].customdata;
          if (slug && window.openControllerPage) {
            window.openControllerPage(slug);
          }
        });
      }"
    )

  htmltools::tagList(
    htmltools::tags$div(class = "bg-compare-note", "Scatter size reflects SD. Click a point to open that controller page."),
    htmltools::tags$div(id = "bg-visual-compare", class = "bg-visual-compare-wrap", p_buyer_scatter)
  )
}
```

```{r buyers-guide-js, echo=FALSE}
htmltools::HTML('
<script>
(function() {
  var THEME_KEY = "inputlatency-theme";
  var DENSITY_KEY = "inputlatency-density";
  var defaultState = { category: ["all"], connection: ["all"], platform: ["all"], face: ["all"], home: ["all"], analog: ["all"] };
  var state = { category: ["all"], connection: ["all"], platform: ["all"], face: ["all"], home: ["all"], analog: ["all"] };
  var activeControllerSlug = "";

  function normalize(x) {
    return (x || "").toLowerCase().trim();
  }

  function getControl(id) {
    return document.getElementById(id);
  }

  function getStoredTheme() {
    try {
      return localStorage.getItem(THEME_KEY);
    } catch (e) {
      return null;
    }
  }

  function getPreferredTheme() {
    var stored = getStoredTheme();
    if (stored === "light" || stored === "dark") {
      return stored;
    }
    return (window.matchMedia && window.matchMedia("(prefers-color-scheme: dark)").matches) ? "dark" : "light";
  }

  function getStoredDensity() {
    try {
      return localStorage.getItem(DENSITY_KEY);
    } catch (e) {
      return null;
    }
  }

  function getPreferredDensity() {
    var density = getStoredDensity();
    return (density === "compact" || density === "comfortable") ? density : "comfortable";
  }

  function updateThemeButton(theme) {
    var btn = getControl("theme-toggle");
    if (!btn) return;
    if (theme === "dark") {
      btn.textContent = "Switch to Light";
      btn.setAttribute("aria-label", "Switch to light theme");
    } else {
      btn.textContent = "Switch to Dark";
      btn.setAttribute("aria-label", "Switch to dark theme");
    }
  }

  function updateDensityButton(density) {
    var btn = getControl("density-toggle");
    if (!btn) return;
    if (density === "compact") {
      btn.textContent = "Density: Compact";
      btn.setAttribute("aria-label", "Switch to comfortable density");
    } else {
      btn.textContent = "Density: Comfortable";
      btn.setAttribute("aria-label", "Switch to compact density");
    }
  }

  function applyPlotlyTheme(theme) {
    if (typeof window.inputLatencyRepaintPlots === "function") {
      window.inputLatencyRepaintPlots(document);
      return;
    }
    if (typeof Plotly === "undefined") return;
    var dark = theme === "dark";
    var baseLayout = {
      paper_bgcolor: dark ? "#151b29" : "#ffffff",
      plot_bgcolor: dark ? "#151b29" : "#ffffff",
      font: { color: dark ? "#e6edf8" : "#101622" }
    };
    document.querySelectorAll(".plotly-graph-div").forEach(function(el) {
      Plotly.relayout(el, baseLayout);
    });
  }

  function applyTheme(theme, persist) {
    document.documentElement.setAttribute("data-theme", theme);
    updateThemeButton(theme);
    if (persist) {
      try { localStorage.setItem(THEME_KEY, theme); } catch (e) {}
    }
    applyPlotlyTheme(theme);
    if (typeof CustomEvent !== "undefined") {
      document.dispatchEvent(new CustomEvent("inputlatency:theme", { detail: { theme: theme } }));
    }
  }

  function applyDensity(density, persist) {
    document.documentElement.setAttribute("data-density", density);
    updateDensityButton(density);
    if (persist) {
      try { localStorage.setItem(DENSITY_KEY, density); } catch (e) {}
    }
  }

  window.toggleTheme = function() {
    var current = document.documentElement.getAttribute("data-theme") || "light";
    var next = current === "dark" ? "light" : "dark";
    applyTheme(next, true);
  };

  window.toggleDensity = function() {
    var current = document.documentElement.getAttribute("data-density") || "comfortable";
    var next = current === "compact" ? "comfortable" : "compact";
    applyDensity(next, true);
  };

  function splitAttrValues(raw) {
    return String(raw || "")
      .split("|")
      .map(function(v) { return v.trim(); })
      .filter(function(v) { return v.length > 0; });
  }

  function matchesState(dim, values) {
    if (!state[dim] || state[dim].indexOf("all") >= 0) return true;
    if (!values || values.length === 0) return false;
    return state[dim].some(function(v) { return values.indexOf(v) >= 0; });
  }

  function getCardBySlug(slug) {
    if (!slug) return null;
    return document.querySelector(".bg-card[data-controller-slug=\\\"" + slug + "\\\"]");
  }

  function getBuyerScatterPlot() {
    var wrap = document.getElementById("bg-visual-compare");
    if (!wrap) return null;
    return wrap.querySelector(".plotly-graph-div");
  }

  function syncScatterToVisibleCards(visibleCards) {
    if (typeof Plotly === "undefined") return;
    var plot = getBuyerScatterPlot();
    if (!plot || !plot.data || !plot.data.length) return;
    var trace = plot.data[0];
    if (!trace || !Array.isArray(trace.customdata)) return;

    var visibleMap = {};
    visibleCards.forEach(function(card) {
      visibleMap[String(card.getAttribute("data-controller-slug") || "")] = true;
    });

    var opacity = trace.customdata.map(function(slug) {
      return visibleMap[String(slug)] ? 0.95 : 0.15;
    });
    Plotly.restyle(plot, { "marker.opacity": [opacity] }, [0]);
  }

  function buildDetailActions(card) {
    if (!card) return "";
    var rawHref = card.getAttribute("data-raw-target-href") || "#raw-data-deep-dive";
    var rawClick = card.getAttribute("data-raw-target-onclick") || "return openTabSection(\\\"raw-data-deep-dive\\\");";
    var rawText = card.getAttribute("data-raw-target-text") || "Open Raw Deep Dive";
    var controllerUrl = card.getAttribute("data-controller-url") || "";
    var buyUrl = card.getAttribute("data-buy-url") || "";

    var parts = [];
    parts.push("<a class=\\\"bg-detail-raw\\\" href=\\\"" + rawHref + "\\\" onclick=\\\"" + rawClick + "\\\">" + rawText + "</a>");
    if (controllerUrl) {
      parts.push("<a href=\\\"" + controllerUrl + "\\\" target=\\\"_blank\\\">Controller Link</a>");
    }
    if (buyUrl && buyUrl !== controllerUrl) {
      parts.push("<a href=\\\"" + buyUrl + "\\\" target=\\\"_blank\\\">Buy Link</a>");
    }
    return parts.join("");
  }

  function parseControllerSlug(id) {
    var m = String(id || "").match(/^controller-([a-z0-9][a-z0-9-]*)$/);
    return m ? m[1] : "";
  }

  window.openControllerPage = function(slug, opts) {
    opts = opts || {};
    var clean = String(slug || "").toLowerCase().replace(/[^a-z0-9-]+/g, "");
    if (!clean) return false;

    var card = getCardBySlug(clean);
    if (!card) return false;

    showTabById("buyers-guide");
    activeControllerSlug = clean;

    var detailRoot = getControl("bg-controller-detail");
    var titleEl = getControl("bg-controller-detail-title");
    var metaEl = getControl("bg-controller-detail-meta");
    var actionsEl = getControl("bg-controller-detail-actions");
    var bodyEl = getControl("bg-controller-detail-body");
    var template = getControl("bg-controller-template-" + clean);
    if (!detailRoot || !titleEl || !metaEl || !actionsEl || !bodyEl || !template) return false;

    var nameEl = card.querySelector(".bg-card-name");
    var metricsEl = card.querySelector(".bg-card-metrics");
    var modeEl = card.querySelector(".bg-card-mode");
    var cat = card.getAttribute("data-category") || "";
    var conn = card.getAttribute("data-connection") || "";
    var face = splitAttrValues(card.getAttribute("data-face"));
    var home = splitAttrValues(card.getAttribute("data-home"));
    var analog = splitAttrValues(card.getAttribute("data-analog"));

    titleEl.textContent = nameEl ? nameEl.textContent : "Controller";
    var metaParts = [];
    if (metricsEl && metricsEl.textContent) metaParts.push(metricsEl.textContent);
    if (cat) metaParts.push(cat);
    if (conn) metaParts.push(conn);
    if (face.length > 0) metaParts.push("Face Buttons: " + face[0]);
    if (home.length > 0) metaParts.push("Home Button: " + home[0]);
    if (analog.length > 0) metaParts.push("Analog: " + analog[0]);
    if (modeEl && modeEl.textContent) metaParts.push(modeEl.textContent);
    metaEl.textContent = metaParts.join(" | ");

    actionsEl.innerHTML = buildDetailActions(card);
    bodyEl.innerHTML = template.innerHTML;
    detailRoot.hidden = false;

    if (window.history && typeof window.history.replaceState === "function" && opts.updateHash !== false) {
      try {
        window.history.replaceState(null, "", "#controller-" + clean);
      } catch (e) {}
    }

    window.setTimeout(function() {
      if (typeof detailRoot.scrollIntoView === "function") {
        detailRoot.scrollIntoView({ behavior: "smooth", block: "start" });
      }
    }, 90);

    return false;
  };

  window.closeControllerPage = function() {
    activeControllerSlug = "";
    var detailRoot = getControl("bg-controller-detail");
    var titleEl = getControl("bg-controller-detail-title");
    var metaEl = getControl("bg-controller-detail-meta");
    var actionsEl = getControl("bg-controller-detail-actions");
    var bodyEl = getControl("bg-controller-detail-body");
    if (detailRoot) detailRoot.hidden = true;
    if (titleEl) titleEl.textContent = "";
    if (metaEl) metaEl.textContent = "";
    if (actionsEl) actionsEl.innerHTML = "";
    if (bodyEl) bodyEl.innerHTML = "";
    if (window.history && typeof window.history.replaceState === "function") {
      try {
        window.history.replaceState(null, "", "#buyers-guide");
      } catch (e) {}
    }
    return false;
  };

  function showTabById(id) {
    var links = document.querySelectorAll(".nav-tabs a");
    var link = null;
    for (var i = 0; i < links.length; i++) {
      if (links[i].getAttribute("href") === "#" + id) {
        link = links[i];
        break;
      }
    }
    if (!link) return;
    if (window.jQuery && typeof window.jQuery(link).tab === "function") {
      window.jQuery(link).tab("show");
    } else if (typeof link.click === "function") {
      link.click();
    }
  }

  function parseRawDistributionSlug(id) {
    var m = String(id || "").match(/^raw-dist-([a-z0-9][a-z0-9-]*)$/);
    return m ? m[1] : "";
  }

  function getRawDistributionDeviceName(slug) {
    if (!slug) return "";
    var anchor = document.getElementById("raw-dist-" + slug);
    if (!anchor) return "";
    return String(anchor.getAttribute("data-raw-device") || "").trim();
  }

  function getRawDistributionPlot() {
    var section = document.getElementById("latency-distribution-by-device");
    if (!section) return null;
    return section.querySelector(".plotly-graph-div");
  }

  function setRawDistributionDevice(deviceName) {
    if (!deviceName || typeof Plotly === "undefined") return false;
    var plot = getRawDistributionPlot();
    if (!plot || !Array.isArray(plot.data) || plot.data.length === 0) return false;

    var idx = -1;
    for (var i = 0; i < plot.data.length; i++) {
      if (plot.data[i] && plot.data[i].name === deviceName) {
        idx = i;
        break;
      }
    }
    if (idx < 0) return false;

    var visibility = plot.data.map(function(_, traceIdx) {
      return traceIdx === idx;
    });
    Plotly.restyle(plot, "visible", visibility);

    if (plot.layout && Array.isArray(plot.layout.updatemenus) && plot.layout.updatemenus.length > 0) {
      var update = {};
      update["updatemenus[0].active"] = idx;
      Plotly.relayout(plot, update);
    }

    return true;
  }

  function scheduleRawDistributionFocus(slug) {
    if (!slug) return;
    var tries = 0;
    function attempt() {
      tries += 1;
      var deviceName = getRawDistributionDeviceName(slug);
      if (setRawDistributionDevice(deviceName)) return;
      if (tries < 12) {
        window.setTimeout(attempt, 160);
      }
    }
    window.setTimeout(attempt, 120);
  }

  window.openRawDistribution = function(slug) {
    var clean = String(slug || "").toLowerCase().replace(/[^a-z0-9-]+/g, "");
    if (!clean) {
      return window.openTabSection("latency-distribution-by-device");
    }
    window.openTabSection("raw-dist-" + clean);
    scheduleRawDistributionFocus(clean);
    return false;
  };

  window.openTabSection = function(targetId) {
    var id = String(targetId || "").replace(/^#/, "");
    if (!id) return true;

    var controllerSlug = parseControllerSlug(id);
    if (controllerSlug) {
      showTabById("buyers-guide");
      window.openControllerPage(controllerSlug, { updateHash: false });
      if (window.history && typeof window.history.replaceState === "function") {
        try {
          window.history.replaceState(null, "", "#controller-" + controllerSlug);
        } catch (e) {
          window.location.hash = "controller-" + controllerSlug;
        }
      } else {
        window.location.hash = "controller-" + controllerSlug;
      }
      return false;
    }

    var rawSlug = parseRawDistributionSlug(id);
    var target = document.getElementById(id);
    if (rawSlug) {
      target = document.getElementById("latency-distribution-by-device") || target;
    }
    if (!target) return true;

    var ancestorIds = [];
    var node = target;
    while (node) {
      if (node.id) ancestorIds.unshift(node.id);
      node = node.parentElement;
    }
    ancestorIds.forEach(function(ancestorId) {
      showTabById(ancestorId);
    });

    if (window.history && typeof window.history.replaceState === "function") {
      try {
        window.history.replaceState(null, "", "#" + id);
      } catch (e) {
        window.location.hash = id;
      }
    } else {
      window.location.hash = id;
    }

    window.setTimeout(function() {
      if (typeof target.scrollIntoView === "function") {
        target.scrollIntoView({ behavior: "smooth", block: "start" });
      }
    }, 140);
    if (rawSlug) {
      scheduleRawDistributionFocus(rawSlug);
    }
    return false;
  };

  function sortCards(cards, sortBy) {
    function numAttr(card, key, fallback) {
      var val = parseFloat(card.getAttribute(key));
      return Number.isFinite(val) ? val : fallback;
    }

    cards.sort(function(a, b) {
      if (sortBy === "latency_desc") {
        return numAttr(b, "data-latency", -Infinity) - numAttr(a, "data-latency", -Infinity);
      }
      if (sortBy === "ontime_desc") {
        return numAttr(b, "data-ontime", -Infinity) - numAttr(a, "data-ontime", -Infinity);
      }
      if (sortBy === "price_asc") {
        return numAttr(a, "data-price", Infinity) - numAttr(b, "data-price", Infinity);
      }
      return numAttr(a, "data-latency", Infinity) - numAttr(b, "data-latency", Infinity);
    });
  }

  window.toggleFilter = function(dim, val, btn) {
    var btns = document.querySelectorAll(".filter-btn[data-dim=\'" + dim + "\']");
    btns.forEach(function(b) { b.classList.remove("active"); });
    if (btn) btn.classList.add("active");
    state[dim] = [val];
    applyFilters();
  };

  window.resetFilters = function() {
    state = {
      category: defaultState.category.slice(),
      connection: defaultState.connection.slice(),
      platform: defaultState.platform.slice(),
      face: defaultState.face.slice(),
      home: defaultState.home.slice(),
      analog: defaultState.analog.slice()
    };

    ["category", "connection", "platform", "face", "home", "analog"].forEach(function(dim) {
      var btns = document.querySelectorAll(".filter-btn[data-dim=\'" + dim + "\']");
      btns.forEach(function(b) {
        b.classList.remove("active");
        if (b.getAttribute("data-val") === "all") {
          b.classList.add("active");
        }
      });
    });

    var search = getControl("bg-search");
    var sort = getControl("bg-sort");
    if (search) search.value = "";
    if (sort) sort.value = "latency_asc";

    applyFilters();
  };

  window.applyFilters = function() {
    var grid = document.getElementById("bg-card-grid");
    if (!grid) return;

    var cards = Array.prototype.slice.call(grid.querySelectorAll(".bg-card"));
    var total = cards.length;
    var shown = 0;
    var searchTerm = normalize(getControl("bg-search") ? getControl("bg-search").value : "");
    var sortBy = getControl("bg-sort") ? getControl("bg-sort").value : "latency_asc";
    var visibleCards = [];

    cards.forEach(function(card) {
      var catMatch = matchesState("category", [String(card.getAttribute("data-category") || "")]);
      var connMatch = matchesState("connection", [String(card.getAttribute("data-connection") || "")]);
      var faceMatch = matchesState("face", splitAttrValues(card.getAttribute("data-face")));
      var homeMatch = matchesState("home", splitAttrValues(card.getAttribute("data-home")));
      var analogMatch = matchesState("analog", splitAttrValues(card.getAttribute("data-analog")));
      var searchMatch = !searchTerm ||
                        normalize(card.getAttribute("data-search")).indexOf(searchTerm) >= 0;
      var platMatch = true;
      if (state.platform.indexOf("all") < 0) {
        var cardPlats = (card.getAttribute("data-platforms") || "").split(",").map(function(p) {
          return p.trim();
        }).filter(function(p) { return p.length > 0; });
        platMatch = state.platform.some(function(p) { return cardPlats.indexOf(p) >= 0; });
      }
      if (catMatch && connMatch && platMatch && faceMatch && homeMatch && analogMatch && searchMatch) {
        visibleCards.push(card);
      } else {
        card.style.display = "none";
      }
    });

    sortCards(visibleCards, sortBy);
    visibleCards.forEach(function(card, idx) {
      card.style.display = "";
      card.querySelector(".bg-card-rank").textContent = "#" + (idx + 1);
      card.style.setProperty("--stagger", String(idx % 12));
      card.style.animation = "none";
      card.offsetHeight;
      card.style.animation = "";
      grid.appendChild(card);
      shown++;
    });

    syncScatterToVisibleCards(visibleCards);
    if (activeControllerSlug) {
      var activeCard = getCardBySlug(activeControllerSlug);
      if (!activeCard || activeCard.style.display === "none") {
        window.closeControllerPage();
      }
    }

    var counter = document.getElementById("bg-counter");
    if (counter) {
      counter.textContent = "Showing " + shown + " of " + total + " devices";
    }
    var matchCounter = document.getElementById("bg-match-counter");
    if (matchCounter) {
      matchCounter.textContent = searchTerm ? "Search: \\"" + searchTerm + "\\"" : "";
    }
  };

  function bindControls() {
    var search = getControl("bg-search");
    var sort = getControl("bg-sort");
    if (search) search.addEventListener("input", applyFilters);
    if (sort) sort.addEventListener("change", applyFilters);
  }

  function syncSystemThemeWhenUnpinned() {
    if (!window.matchMedia) return;
    var media = window.matchMedia("(prefers-color-scheme: dark)");
    var cb = function(e) {
      var stored = getStoredTheme();
      if (stored === "light" || stored === "dark") return;
      applyTheme(e.matches ? "dark" : "light", false);
    };
    if (media.addEventListener) {
      media.addEventListener("change", cb);
    } else if (media.addListener) {
      media.addListener(cb);
    }
  }

  var initialized = false;
  function initializeDashboard() {
    if (initialized) return;
    initialized = true;

    applyTheme(getPreferredTheme(), false);
    applyDensity(getPreferredDensity(), false);
    bindControls();
    applyFilters();
    syncSystemThemeWhenUnpinned();
    setTimeout(function() {
      applyPlotlyTheme(document.documentElement.getAttribute("data-theme") || "light");
    }, 200);
    function openCurrentHash() {
      if (window.location && window.location.hash) {
        window.openTabSection(window.location.hash);
      }
    }
    setTimeout(openCurrentHash, 260);
    setTimeout(openCurrentHash, 700);
  }

  document.addEventListener("DOMContentLoaded", initializeDashboard);
  window.addEventListener("hashchange", function() {
    if (window.location && window.location.hash) {
      window.openTabSection(window.location.hash);
    }
  });

  if (document.readyState !== "loading") {
    initializeDashboard();
  }
})();
</script>
')
```

## Detailed Analysis

### Latency Overview

If you see a controller you'd like more info on, its row value listed here will match the "Detailed Results" tab in the spreadsheet.

```{r latency-filters-detail, echo=FALSE}
keep <- c("Device", "Latency (in ms)", "SD", "Category", "Connection", "Latency Tier", "Row")
keep_logical <- names(dat) %in% keep

shared_dat_detail <- SharedData$new(dat, group = "detail_table")
bscols(widths = c(12),
  list(
    filter_select("MakeDetail", "Make", shared_dat_detail, ~Make),
    filter_select("ConnectionDetail", "Wired/Wireless", shared_dat_detail, ~`Wired/Wireless`,
                  multiple = TRUE),
    filter_select("HomeButtonDetail", "Home Button", shared_dat_detail, ~`Home Button`,
                  multiple = TRUE),
    filter_select("CategoryDetail", "Category", shared_dat_detail, ~Category,
                  multiple = TRUE),
    filter_select("FaceButtonsDetail", "Face Buttons", shared_dat_detail, ~`Face Buttons`,
                  multiple = TRUE),
    filter_select("LatencyTierDetail", "Latency Tier", shared_dat_detail, ~`Latency Tier`,
                  multiple = TRUE)
  )
)

datatable(shared_dat_detail,
          options = list(
            autowidth = TRUE,
            fixedColumns = TRUE,
            pageLength = 25,
            columnDefs = list(list(visible = FALSE,
                                   targets = (1:ncol(dat))[!keep_logical]))
          ),
          escape = FALSE)
```

### Recently Added

```{r recently-added-detail, echo=FALSE}
keep_logical_recent <- names(dat) %in% c(keep, "Date Added")

datatable(dat[rev(order(as.Date(dat$`Date Added`, format = "%m/%d/%Y"))), ],
          options = list(
            autowidth = TRUE,
            fixedColumns = TRUE,
            pageLength = 20,
            columnDefs = list(list(visible = FALSE,
                                   targets = (1:ncol(dat))[!keep_logical_recent]))
          ),
          escape = FALSE)
```

### Summary Statistics

```{r summary-stats, echo=FALSE, warning=FALSE}
# Wired vs Wireless statistical comparison
wired_latency <- dat %>% filter(`Wired/Wireless` == "Wired") %>% pull(`Latency (in ms)`)
wireless_latency <- dat %>% filter(`Wired/Wireless` == "Wireless") %>% pull(`Latency (in ms)`)

if (length(wired_latency) > 2 && length(wireless_latency) > 2) {
  t_result <- t.test(wired_latency, wireless_latency)
}
```

**Overall Statistics:**

- Total devices tested: `r nrow(dat)`
- Wired devices: `r sum(dat$'Wired/Wireless' == "Wired", na.rm = TRUE)` (mean latency: `r round(mean(wired_latency, na.rm = TRUE), 2)` ms)
- Wireless devices: `r sum(dat$'Wired/Wireless' == "Wireless", na.rm = TRUE)` (mean latency: `r round(mean(wireless_latency, na.rm = TRUE), 2)` ms)
- Devices with raw capture backing: `r sum(dat$HasRawCapture, na.rm = TRUE)` (`r raw_coverage_pct`%)
- One frame threshold: `r round(100/6, 2)` ms (60 Hz)

```{r wired-wireless-ttest, echo=FALSE, results='asis'}
if (exists("t_result")) {
  cat(sprintf("\n**Wired vs Wireless t-test:** t = %.2f, p-value = %.4f %s\n",
              t_result$statistic,
              t_result$p.value,
              ifelse(t_result$p.value < 0.05, "(statistically significant)", "(not significant)")))
}
```

```{r category-summary, echo=FALSE}
category_stats <- dat %>%
  group_by(Category) %>%
  summarise(
    Count = n(),
    `Mean Latency` = round(mean(`Latency (in ms)`, na.rm = TRUE), 2),
    `Median Latency` = round(median(`Latency (in ms)`, na.rm = TRUE), 2),
    `Min` = round(min(`Latency (in ms)`, na.rm = TRUE), 2),
    `Max` = round(max(`Latency (in ms)`, na.rm = TRUE), 2),
    .groups = 'drop'
  ) %>%
  arrange(`Mean Latency`)

datatable(category_stats,
          options = list(pageLength = 10, dom = 't'),
          caption = "Latency by Category")
```

### Interactive Charts {.tabset}

In all plots, the dashed red line corresponds to one frame (16.67 ms at 60 Hz).

#### Wired vs. Wireless

```{r wired-wireless-plotly, echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
p_wired <- dat %>%
  filter(!is.na(`Wired/Wireless`)) %>%
  ggplot(aes(x = `Wired/Wireless`, y = `Latency (in ms)`,
             color = `Wired/Wireless`, text = DeviceClean)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.2, alpha = 0.6, size = 2) +
  scale_color_manual(values = connection_colors) +
  geom_hline(yintercept = 100 / 6, color = '#BA1B1D', linetype = "dashed") +
  labs(title = "Wired vs. Wireless Latency Distribution") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 12))

ggplotly(p_wired, tooltip = c("text", "y"), width = 1000, height = 500) %>%
  layout(hovermode = "closest")
```

#### 2.4GHz vs. Bluetooth

```{r bt-vs-24ghz-plotly, echo=FALSE, fig.height=8, fig.width=12, warning=FALSE}
wireless_dat <- dat %>%
  filter(WirelessConnection %in% c("Bluetooth", "2.4 GHz"))

if (nrow(wireless_dat) > 0) {
  p_wireless <- wireless_dat %>%
    ggplot(aes(x = WirelessConnection, y = `Latency (in ms)`,
               color = WirelessConnection, text = DeviceClean)) +
    geom_boxplot(outlier.shape = NA) +
    geom_jitter(width = 0.2, alpha = 0.6, size = 2) +
    scale_color_manual(values = wireless_type_colors) +
    geom_hline(yintercept = 100 / 6, color = '#BA1B1D', linetype = "dashed") +
    xlab("Wireless Type") +
    ylab("Latency (in ms)") +
    labs(title = "2.4GHz Wireless vs. Bluetooth Latency") +
    theme_minimal() +
    theme(legend.position = "none",
          axis.text = element_text(size = 11),
          axis.title = element_text(size = 12))

  ggplotly(p_wireless, tooltip = c("text", "y"), width = 1000, height = 500) %>%
    layout(hovermode = "closest")
}
```

#### Latency by Rank

```{r latency-rank-plotly, echo=FALSE, fig.width=14, warning=FALSE}
dat_ranked <- dat %>%
  arrange(`Latency (in ms)`) %>%
  mutate(Rank = row_number())

p_rank <- dat_ranked %>%
  ggplot(aes(x = Rank, y = `Latency (in ms)`,
             color = `Wired/Wireless`, text = DeviceClean)) +
  geom_point(alpha = 0.7, size = 2.5) +
  scale_color_manual(values = connection_colors) +
  geom_hline(yintercept = 100 / 6, color = '#BA1B1D', linetype = "dashed") +
  xlab("Rank (Lower = Better)") +
  ylab("Latency (in ms)") +
  labs(title = "Latency by Rank") +
  theme_minimal() +
  theme(axis.text = element_text(size = 11),
        axis.title = element_text(size = 12))

ggplotly(p_rank, tooltip = c("text", "y", "x"), width = 1200, height = 500) %>%
  layout(hovermode = "closest")
```

#### Category Comparison

```{r category-boxplot-plotly, echo=FALSE, fig.height=10, fig.width=14, warning=FALSE}
p_category <- dat %>%
  filter(!is.na(Category)) %>%
  ggplot(aes(x = reorder(Category, `Latency (in ms)`, FUN = median),
             y = `Latency (in ms)`, fill = Category, text = DeviceClean)) +
  geom_boxplot(alpha = 0.7, outlier.shape = NA) +
  geom_jitter(width = 0.2, alpha = 0.6, size = 2) +
  scale_fill_manual(values = category_colors) +
  geom_hline(yintercept = 100 / 6, color = '#BA1B1D', linetype = "dashed") +
  coord_flip() +
  labs(title = "Latency Distribution by Category",
       x = "Category", y = "Latency (in ms)") +
  theme_minimal() +
  theme(legend.position = "none",
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 12))

ggplotly(p_category, tooltip = c("text", "y"), width = 1200, height = 600) %>%
  layout(hovermode = "closest")
```

### Raw Data Deep Dive

This section analyzes the raw capture data from individual controller tests, providing detailed latency distribution insights.

```{r raw-data-available, echo=FALSE}
n_devices_raw <- length(unique(raw_data$Device))
n_readings <- nrow(raw_data)
```

**Raw data available:** `r n_devices_raw` devices with `r format(n_readings, big.mark = ",")` total readings.

#### Data Coverage

- Devices in database: `r nrow(dat)`
- Devices with matched raw captures: `r sum(dat$HasRawCapture, na.rm = TRUE)` (`r raw_coverage_pct`%)

#### Percentile Statistics from Raw Captures

```{r raw-percentile-table, echo=FALSE}
if (nrow(raw_stats) > 0) {
  raw_stats_display <- raw_stats %>%
    arrange(RawMean) %>%
    select(Device, N, RawMean, Median, P90, P95, P99, Consistency) %>%
    rename(
      `Readings` = N,
      `Mean (ms)` = RawMean,
      `Median (ms)` = Median,
      `P90 (ms)` = P90,
      `P95 (ms)` = P95,
      `P99 (ms)` = P99,
      `Consistency %` = Consistency
    ) %>%
    mutate(across(where(is.numeric), ~round(., 2)))

  datatable(raw_stats_display,
            options = list(pageLength = 15, scrollX = TRUE),
            caption = "Percentile statistics from raw capture data (lower is better, higher consistency is better)")
}
```

#### Latency Distribution by Device

Select a device to view its latency distribution histogram.

```{r raw-device-distribution-anchors, echo=FALSE, results='asis'}
if (exists("raw_device_index") && nrow(raw_device_index) > 0) {
  anchors <- vapply(seq_len(nrow(raw_device_index)), function(i) {
    slug <- raw_device_index$DeviceSlug[[i]]
    dev <- raw_device_index$Device[[i]]
    sprintf(
      '<span id="raw-dist-%s" data-raw-device="%s"></span>',
      htmltools::htmlEscape(slug),
      htmltools::htmlEscape(dev)
    )
  }, character(1))
  cat(
    '<div class="bg-raw-device-anchor-index" aria-hidden="true" style="display:none;">',
    paste(anchors, collapse = ""),
    '</div>'
  )
}
```

```{r raw-histogram-interactive, echo=FALSE, warning=FALSE}
if (nrow(raw_data) > 0) {
  # Get all devices sorted by mean latency
  device_list <- raw_stats %>%
    arrange(RawMean) %>%
    pull(Device)

  # Pre-bin histograms to reduce page size vs embedding full raw vectors
  max_delay <- max(raw_data$delay, na.rm = TRUE)
  hist_breaks <- seq(0, max(40, ceiling(max_delay)), by = 0.5)
  hist_cache <- lapply(device_list, function(dev) {
    dev_delay <- raw_data %>% filter(Device == dev) %>% pull(delay)
    h <- hist(dev_delay, breaks = hist_breaks, plot = FALSE)
    tibble::tibble(mid = h$mids, count = h$counts)
  })

  # Create dropdown buttons
  buttons <- lapply(seq_along(device_list), function(i) {
    visibility <- rep(FALSE, length(device_list))
    visibility[i] <- TRUE
    list(
      method = "update",
      args = list(list(visible = visibility)),
      label = truncate_name(device_list[i], 50)
    )
  })

  # Combine all traces
  p_hist <- plot_ly()
  for (i in seq_along(device_list)) {
    hdat <- hist_cache[[i]]
    p_hist <- p_hist %>%
      add_bars(
        x = hdat$mid,
        y = hdat$count,
        name = device_list[i],
        visible = (i == 1),
        marker = list(color = '#3498DB')
      )
  }

  p_hist %>%
    layout(
      title = list(text = "Latency Distribution", y = 0.95),
      xaxis = list(title = "Latency (ms)"),
      yaxis = list(title = "Count"),
      showlegend = FALSE,
      shapes = list(
        list(type = "line", x0 = 100/6, x1 = 100/6, y0 = 0, y1 = 1,
             yref = "paper", line = list(color = "#BA1B1D", dash = "dash", width = 2))
      ),
      updatemenus = list(
        list(
          type = "dropdown",
          active = 0,
          buttons = buttons,
          x = 0.0,
          xanchor = "left",
          y = 1.15,
          yanchor = "top"
        )
      ),
      annotations = list(
        list(text = "Select Device:", x = 0, xref = "paper", xanchor = "left",
             y = 1.22, yref = "paper", showarrow = FALSE)
      ),
      margin = list(t = 100)
    )
}
```

#### Time-Series Pattern Viewer

Select a device to view its latency over time. Look for periodic sawtooth patterns indicating polling intervals.

```{r raw-timeseries-interactive, echo=FALSE, warning=FALSE}
if (nrow(raw_data) > 0) {
  downsample_device_series <- function(df, max_points = 300) {
    if (nrow(df) <= max_points) {
      return(df)
    }
    idx <- unique(round(seq(1, nrow(df), length.out = max_points)))
    df[idx, , drop = FALSE]
  }

  # Get devices with at least 100 readings (cap count for page size)
  devices_with_data <- raw_data %>%
    count(Device) %>%
    filter(n >= 100) %>%
    arrange(desc(n), Device) %>%
    slice_head(n = 20) %>%
    pull(Device)

  # Create dropdown buttons
  buttons_ts <- lapply(seq_along(devices_with_data), function(i) {
    visibility <- rep(FALSE, length(devices_with_data))
    visibility[i] <- TRUE
    list(
      method = "update",
      args = list(list(visible = visibility)),
      label = truncate_name(devices_with_data[i], 50)
    )
  })

  # Build plot with all device traces
  p_ts <- plot_ly()
  for (i in seq_along(devices_with_data)) {
    dev_data <- raw_data %>%
      filter(Device == devices_with_data[i]) %>%
      arrange(read) %>%
      downsample_device_series(max_points = 300)

    p_ts <- p_ts %>%
      add_trace(x = dev_data$read, y = dev_data$delay,
                type = 'scatter', mode = 'lines+markers',
                name = devices_with_data[i],
                visible = (i == 1),
                line = list(color = '#3498DB', width = 1),
                marker = list(color = '#3498DB', size = 3))
  }

  p_ts %>%
    layout(
      title = list(text = "Latency Time Series (Downsampled to 300 Points)", y = 0.95),
      xaxis = list(title = "Reading Number"),
      yaxis = list(title = "Latency (ms)"),
      showlegend = FALSE,
      shapes = list(
        list(type = "line", x0 = 0, x1 = 1, xref = "paper",
             y0 = 100/6, y1 = 100/6,
             line = list(color = "#BA1B1D", dash = "dash", width = 2))
      ),
      updatemenus = list(
        list(
          type = "dropdown",
          active = 0,
          buttons = buttons_ts,
          x = 0.0,
          xanchor = "left",
          y = 1.15,
          yanchor = "top"
        )
      ),
      annotations = list(
        list(text = "Select Device:", x = 0, xref = "paper", xanchor = "left",
             y = 1.22, yref = "paper", showarrow = FALSE)
      ),
      margin = list(t = 100),
      height = 500
    )
}
```

#### Consistency Analysis

Devices with higher consistency scores have more predictable latency (less variance relative to mean).

```{r consistency-plotly, echo=FALSE, fig.width=12, warning=FALSE}
if (nrow(raw_stats) > 0) {
  p_consistency <- raw_stats %>%
    filter(!is.na(Consistency)) %>%
    mutate(DeviceShort = truncate_name(Device, 40)) %>%
    ggplot(aes(x = RawMean, y = Consistency, text = DeviceShort)) +
    geom_point(aes(size = N), alpha = 0.7, color = '#2708A0') +
    geom_hline(yintercept = 90, color = '#22A722', linetype = "dashed") +
    geom_vline(xintercept = 100 / 6, color = '#BA1B1D', linetype = "dashed") +
    labs(title = "Latency vs Consistency",
         subtitle = "Green line: 90% consistency threshold. Red line: one frame.",
         x = "Mean Latency (ms)", y = "Consistency Score (%)",
         size = "# Readings") +
    theme_minimal() +
    theme(axis.text = element_text(size = 10),
          axis.title = element_text(size = 11))

  ggplotly(p_consistency, tooltip = c("text", "x", "y"), width = 1200, height = 500) %>%
    layout(hovermode = "closest")
}
```

### Latency Ranges

These plots show approximate latency ranges using 95% confidence intervals. Due to limited data, some standard deviations were imputed using linear regression. Imputed values are shown in a different color.

Use the filters below to show specific device types and connection methods.

```{r latency-range-filters, echo=FALSE}
# Prepare data for filtered plot - sort by latency and set factor levels
range_plot_dat <- dat %>%
  filter(!is.na(`Wired/Wireless`), !is.na(Category)) %>%
  mutate(
    DeviceLabel = gsub("<[^>]+>", "", Device),
    DeviceShort = truncate_name(DeviceLabel, 45)
  ) %>%
  arrange(`Latency (in ms)`) %>%
  mutate(DeviceShort = factor(DeviceShort, levels = rev(unique(DeviceShort))))

# Use a named key so filters and plot share the same crosstalk group
shared_range_dat <- SharedData$new(range_plot_dat, key = ~ID, group = "range_group")

bscols(widths = c(12),
  list(
    filter_select("ConnectionType", "Wired/Wireless", shared_range_dat, ~`Wired/Wireless`, multiple = TRUE),
    filter_select("DeviceCategory", "Category", shared_range_dat, ~Category, multiple = TRUE)
  )
)
```

```{r latency-range-plot, echo=FALSE, fig.height=25, fig.width=14, warning=FALSE}
# Calculate appropriate height
plot_height <- min(2000, max(700, nrow(range_plot_dat) * 14))

# Split data by imputation status for separate legend entries
imputed_data <- range_plot_dat %>% filter(Imputed == TRUE)
measured_data <- range_plot_dat %>% filter(Imputed == FALSE)

shared_imputed <- SharedData$new(imputed_data, key = ~ID, group = "range_group")
shared_measured <- SharedData$new(measured_data, key = ~ID, group = "range_group")

# Build native plot_ly so crosstalk filters work
p_range <- plot_ly(height = plot_height, width = 1400) %>%
  # Error bars for imputed SD
  add_trace(data = shared_imputed,
            x = ~`Latency (in ms)`, y = ~DeviceShort,
            type = 'scatter', mode = 'markers',
            error_x = list(
              type = "data",
              symmetric = FALSE,
              array = ~(`SD up` - `Latency (in ms)`),
              arrayminus = ~(`Latency (in ms)` - `SD down`),
              color = "#E63946", width = 3
            ),
            marker = list(color = "#333", size = 6),
            name = "Imputed SD",
            hovertext = ~paste0(DeviceLabel,
                               "\nLatency: ", round(`Latency (in ms)`, 2), " ms",
                               "\nCategory: ", Category,
                               "\nConnection: ", `Wired/Wireless`),
            hoverinfo = "text") %>%
  # Error bars for measured SD
  add_trace(data = shared_measured,
            x = ~`Latency (in ms)`, y = ~DeviceShort,
            type = 'scatter', mode = 'markers',
            error_x = list(
              type = "data",
              symmetric = FALSE,
              array = ~(`SD up` - `Latency (in ms)`),
              arrayminus = ~(`Latency (in ms)` - `SD down`),
              color = "#457B9D", width = 3
            ),
            marker = list(color = "#333", size = 6),
            name = "Measured SD",
            hovertext = ~paste0(DeviceLabel,
                               "\nLatency: ", round(`Latency (in ms)`, 2), " ms",
                               "\nCategory: ", Category,
                               "\nConnection: ", `Wired/Wireless`),
            hoverinfo = "text") %>%
  layout(
    title = list(text = "Device Latency Ranges (95% CI)<br><sup>Sorted by average latency (lowest first)</sup>"),
    xaxis = list(title = "Latency (ms)"),
    yaxis = list(title = "", tickfont = list(size = 7)),
    hovermode = "closest",
    margin = list(l = 280, t = 80, b = 80),
    shapes = list(
      list(type = "line", x0 = 100/6, x1 = 100/6, y0 = 0, y1 = 1,
           yref = "paper", line = list(color = "#BA1B1D", dash = "dash", width = 2))
    ),
    legend = list(orientation = "h", y = -0.05)
  )

p_range
```

<small>**Note:** Red error bars indicate imputed standard deviation (estimated via linear regression). Blue bars are measured values.</small>

### Best Performers by Category

Top 3 performing devices in each category, separated by wired and wireless connection.

```{r best-performers, echo=FALSE}
# Get top 3 wired devices per category
best_wired <- dat %>%
  filter(`Wired/Wireless` == "Wired", !is.na(Category)) %>%
  group_by(Category) %>%
  slice_min(`Latency (in ms)`, n = 3, with_ties = FALSE) %>%
  mutate(Rank = row_number()) %>%
  ungroup() %>%
  mutate(Connection = "Wired") %>%
  select(Category, Connection, Rank, Device = DeviceClean, `Latency (in ms)`)

# Get top 3 wireless devices per category
best_wireless <- dat %>%
  filter(`Wired/Wireless` == "Wireless", !is.na(Category)) %>%
  group_by(Category) %>%
  slice_min(`Latency (in ms)`, n = 3, with_ties = FALSE) %>%
  mutate(Rank = row_number()) %>%
  ungroup() %>%
  mutate(Connection = "Wireless") %>%
  select(Category, Connection, Rank, Device = DeviceClean, `Latency (in ms)`)

# Combine and arrange
best_performers <- bind_rows(best_wired, best_wireless) %>%
  arrange(Category, Connection, Rank) %>%
  mutate(
    `Latency (in ms)` = round(`Latency (in ms)`, 2),
    Rank = paste0("#", Rank)
  )

datatable(best_performers,
          options = list(
            pageLength = 50,
            dom = 'ft',
            columnDefs = list(
              list(className = 'dt-left', targets = c(0, 1, 3)),
              list(className = 'dt-center', targets = 2),
              list(className = 'dt-right', targets = 4)
            )
          ),
          filter = 'top',
          rownames = FALSE,
          caption = "Top 3 devices per category and connection type (lowest latency)")
```

### Methodology

This data was collected using a closed-loop latency testing system consisting of:

- **Arduino Pro Micro** - Triggers virtual button presses and measures response time via hardware interrupt
- **DE10-nano with MiSTer FPGA** - Running the NES Lag Tester core to detect inputs
- **Custom test PCB** - Connects the Arduino, controller pins, and DE10-nano

The Arduino triggers a button press on the controller under test, and measures the time until the MiSTer core detects the input. Results are captured via serial output in CSV format.

For more details, see the [GitHub repository](https://github.com/misteraddons/inputlatency).

```{r plotly-resize-handler, echo=FALSE}
htmltools::HTML('
<script>
function inputLatencyPlotlyStyle(theme) {
  var dark = theme === "dark";
  return {
    paperBg: dark ? "#151b29" : "#ffffff",
    plotBg: dark ? "#151b29" : "#ffffff",
    fontColor: dark ? "#e6edf8" : "#101622",
    gridColor: dark ? "rgba(186, 204, 235, 0.18)" : "rgba(31, 53, 91, 0.15)",
    zeroColor: dark ? "rgba(186, 204, 235, 0.26)" : "rgba(31, 53, 91, 0.25)",
    legendBg: dark ? "rgba(18, 24, 35, 0.6)" : "rgba(255, 255, 255, 0.6)",
    hoverBg: dark ? "rgba(20, 27, 40, 0.95)" : "rgba(255, 255, 255, 0.95)",
    hoverBorder: dark ? "rgba(200, 181, 255, 0.36)" : "rgba(80, 0, 220, 0.26)",
    colorway: dark
      ? ["#b99eff", "#E6FF1E", "#8f69ff", "#d3eb42", "#ff95c7", "#8ec3ff"]
      : ["#5000DC", "#A2B800", "#6f2cff", "#c3d900", "#af4eff", "#3e4870"]
  };
}

function inputLatencyLayoutPatch(node, style) {
  var patch = {
    paper_bgcolor: style.paperBg,
    plot_bgcolor: style.plotBg,
    "font.color": style.fontColor,
    "legend.font.color": style.fontColor,
    "legend.bgcolor": style.legendBg,
    "legend.bordercolor": style.gridColor,
    "hoverlabel.bgcolor": style.hoverBg,
    "hoverlabel.bordercolor": style.hoverBorder,
    "hoverlabel.font.color": style.fontColor,
    colorway: style.colorway
  };

  var full = node && node._fullLayout ? node._fullLayout : {};
  Object.keys(full).forEach(function(key) {
    if (!/^xaxis\\d*$/.test(key) && !/^yaxis\\d*$/.test(key)) return;
    patch[key + ".gridcolor"] = style.gridColor;
    patch[key + ".linecolor"] = style.gridColor;
    patch[key + ".tickcolor"] = style.gridColor;
    patch[key + ".zerolinecolor"] = style.zeroColor;
    patch[key + ".tickfont.color"] = style.fontColor;
    patch[key + ".title.font.color"] = style.fontColor;
  });

  return patch;
}

function inputLatencyRepaintPlots(scope) {
  if (typeof Plotly === "undefined") return;
  var theme = document.documentElement.getAttribute("data-theme") || "light";
  var style = inputLatencyPlotlyStyle(theme);
  var root = scope || document;
  var nodes = root.querySelectorAll ? root.querySelectorAll(".plotly-graph-div") : [];
  nodes.forEach(function(node) {
    var patch = inputLatencyLayoutPatch(node, style);
    Plotly.Plots.resize(node);
    Plotly.relayout(node, patch);
  });
}

window.inputLatencyRepaintPlots = inputLatencyRepaintPlots;
window.inputLatencyPlotlyStyle = inputLatencyPlotlyStyle;

// Resize and retheme Plotly/DataTables when switching tabs
$(document).on("shown.bs.tab", "a[data-toggle=\'tab\']", function() {
  var pane = $($(this).attr("href"));
  inputLatencyRepaintPlots(pane.get(0));
});

// Keep hidden charts synced with theme changes
document.addEventListener("inputlatency:theme", function() {
  inputLatencyRepaintPlots(document);
});
</script>
')
```
